### 2022-11-22 research/manuscript-example/main.tex
add example latex manuscript

\documentclass[conf]{new-aiaa}
%\documentclass[journal]{new-aiaa} for journal papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt}

\title{Preparation of Papers for AIAA Technical Conferences}

\author{First A. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B. Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
\affil{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affil{Business or Academic Affiliation 2, City, State, Zip Code}

\begin{document}

\maketitle

\begin{abstract}
These instructions give you guidelines for preparing papers for AIAA Technical Papers using \LaTeX{}. Define all symbols used in the abstract. Do not cite references in the abstract. The footnote on the first page should list the Job Title and AIAA Member Grade for each author, if known Authors do not have to be AIAA members.
\end{abstract}

\section{Nomenclature}

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$A$  & amplitude of oscillation \\
$a$ &    cylinder diameter \\
$C_p$& pressure coefficient \\
$Cx$ & force coefficient in the \textit{x} direction \\
$Cy$ & force coefficient in the \textit{y} direction \\
c   & chord \\
d$t$ & time step \\
$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
$f, g$   & generic functions \\
$h$  & height \\
$i$  & time index during navigation \\
$j$  & waypoint index \\
$K$  & trailing-edge (TE) nondimensional angular deflection rate
\end{longtable*}}

\section{Introduction}
\lettrine{T}{his} document is a \LaTeX{} template for preparation of papers for AIAA Technical Conferences. If you are reading a hard-copy or .pdf version of this document, download the electronic file, new-aiaa.cls, and use it to prepare your manuscript.

Authors using \url{https://www.overleaf.com} may simply open the AIAA template from the Overleaf gallery to work online; no local installation of any files is required. Authors using a local \LaTeX{} installation will need to open the template in Overleaf and use the ``Download as zip'' option from the project menu to download a local copy of the template files. To create your formatted manuscript, type your own text over sections of the template, or cut and paste from another document and then use the available markup styles. Note that special formatting such as subscripts, superscripts, and italics may be lost when you copy your text into the template from a Word Processing program such as Microsoft Word. See Sec. V for more detailed formatting guidelines.

\section{Procedure for Paper Submission}

All manuscripts are to be submitted electronically to the ScholarOne Abstracts site created for each conference. The manuscript upload will be enabled several weeks after acceptance notices have been sent. Presenting authors of accepted papers will receive an email with instructions when manuscript submission is open. It is important that presenting authors keep their email addresses up-to- date so they do not miss this notice.

Before completing manuscript submission, submitters must also select the copyright statement that will appear on the paper, and complete other acknowledgments. It is also necessary to click both the ``Accept'' and ``Save'' buttons to complete a submission. All completed manuscript submission will be confirmed by email. Completed submissions will also have a status of ``Accepted'' at the top of your manuscript submission page.

All files must be in pdf format. Please be sure that all security settings are removed from the pdf file before uploading to ensure proper processing of your manuscript file.

\section{General Guidelines}

The following section outlines general (nonformatting) guidelines to follow, drawn from the original AIAA Manuscript Preparation Kit. These guidelines are applicable to all authors (except as noted), and include information on the policies and practices relevant to the publication of your manuscript.

\subsection{Publication by AIAA}
Your manuscript cannot be published by AIAA if:
\begin{enumerate}
\item It has been published previously or

\item The work contains copyright-infringing material or

\item An appropriate copyright statement has not yet been selected.
\end{enumerate}

\subsection{Paper Review and Visa Considerations}

It is the responsibility of the author to obtain any required government or company reviews for their papers in advance of publication. Start early to determine if the reviews are required; this process can take several weeks.

If you plan to attend an AIAA Forum, technical conference or professional development course held in the United States and you require a visa for travel, it is incumbent upon you to apply for a visa with the U.S.~embassy (consular division) or consulate with ample time for processing.  To avoid bureaucratic problems, AIAA strongly suggests that you submit your formal application to U.S.~ authorities a minimum of 120 days in advance of the date of anticipated travel.

Prospective conference and course attendees requiring a visa to travel to the United States should first contact

AIAA to request an official letter of invitation. This letter and a copy of the conference call for papers should be presented along with the required documentation to the U.S. consular officials as part of the formal application process.  AIAA cannot directly intervene with the U.S. Department of State, consular offices, or embassies on behalf of individuals applying for visas. A letter of invitation can be requested by completing the Visa Invitation Letter Request Form at \url{https://www.aiaa.org/Secondary.aspx?id=6258} or you may contact the Event Registrar at \url{invitation@aiaa.org} for more information.

\subsection{Control ID Number vs Paper Number}

Your paper was assigned a control ID number at the time you submitted your abstract. It is critical that you reference the tracking number and conference name when contacting AIAA regarding your submission. The control ID number is \emph{not} the final AIAA paper number. The paper number, which appears in the format AIAA-20XX-XXXX, will be used to refer to your paper in the program and in any publication format. It will not be assigned until shortly before the conference. \textbf{Do not include a paper number anywhere on your paper, as this number will be stamped automatically in the top right corner of your paper at the time of processing.}

\subsection{Copyright}

Before AIAA can print or publish any paper, the copyright information must be completed in the submission system. Failure to complete the electronic form correctly could result in your paper not being published. The following fields must be completed:

\begin{enumerate}
\item Clearance Statement
\item Non-Infringement Statement
\item Publication Status Statement
\item One Copyright Assignment Statement (Select either A, B, C, or D)
\end{enumerate}

Be sure to read the copyright statements carefully. AIAA requires a copyright transfer from the author(s) to AIAA or a license to publish and distribute your material; government authors can assert that the work is in the public domain. If you are not sure which copyright statement to use, contact your legal department. Refer to AIAA’s Rights and Permissions page at \url{www.aiaa.org} for more information; AIAA cannot help you determine which statement to use. Do not include a copyright statement anywhere on your paper. A hard copy of the form is found in the Author Kit for your reference. As you will be completing this form online, you do not need to fill out the hard-copy form. Do not include a copyright statement anywhere on your paper, and do not upload a copyright form with your paper. The correct statement will be stamped automatically at the time of processing.

\subsection{Submission Deadlines}

Manuscripts will be accepted for upload to the system from the receipt of the email invitation until the deadline set for the conference. You will be notified of the specific manuscript submission deadline in your acceptance letter, and the deadline will also be listed on the conference web page at AIAA. Please do not upload a draft version of your manuscript with the intent to upload a final version later. \textbf{Please review your manuscript very carefully before completing your submission to ensure that your paper is complete and final in all respects. Once the manuscript deadline has passed you will be locked out of the manuscript site so it is critical that you upload a final, carefully proofed document.}

Online conference proceedings will be made accessible to attendees who have registered for the ``full conference'' when the conference opens. Once the proceedings are published online, the conference papers will be considered the version of record and may not be removed or replaced. Changes to published papers can be made available through the Crossmark feature, where corrections and updates are accessed by clicking the Crossmark icon available on every paper published in Aerospace Research Central.

The opportunity to submit Crossmark updates will be provided to presenting authors starting the first day of the conference through 2000 hrs/8 pm Eastern Time, seven business days after the last day of the conference.  The proceedings will be updated with Crossmark updates shortly after that date.

AIAA will NOT accept changes and/or change requests that solely correct grammatical errors, spelling errors, or errors in formatting.  All corrections should be for editorially significant changes where the change affects interpretation or crediting of the work.

To ensure conference quality, session chairs will enforce a ``no paper, no podium'' rule. This policy is intended to eliminate no-shows, to improve the quality of the conference for all participants, and to ensure that the published proceedings accurately represent the presentations made at a conference.

\section{Detailed Formatting Instructions}

The styles and formats for the AIAA Papers Template have been incorporated into the structure of this document. If you are using \LaTeX{}, please use this template to prepare your manuscript. A Microsoft Word template is also available from AIAA's website if you prefer to use Microsoft Word 2001 or later. Regardless of which program you use to prepare your manuscript, please use the formatting instructions contained in this document as a guide.

If you are using the AIAA Meeting Papers \LaTeX{} Template file to prepare your manuscript, you can simply type your own text over sections of this document, or cut and paste from another document and use the available markup styles. If you choose to cut and paste, select the text from your original document and choose Edit>Copy. (Do not select your title and author information, since the document spacing may be affected. It is a simple task to reenter your title and author information in the template.) Open the \LaTeX{} template file. Place your cursor in the text area of the template and select Edit>Paste. Please note that special formatting (e.g., subscripts, superscripts, italics) may be lost when you copy your text into the template. Use italics for emphasis; do not underline. Use the compiled \LaTeX{} pdf to see the most accurate representation of how your final paper will appear.

\subsection{Document Text}
The default font for AIAA papers is Times New Roman, 10-point size.  The first line of every paragraph should be indented, and all lines should be single-spaced. Default margins are 1'' on all sides. In the electronic version of this template, all margins and other formatting is preset. There should be no additional lines between paragraphs.

\begin{quoting}
Extended quotes, such as this example, are to be used when material being cited is longer than a few sentences, or the standard quotation format is not practical. In this \LaTeX template, the appropriate command environment is \verb|\begin{quoting}...\end{quoting}|. Extended quotes are to be in Times New Roman, 9-point font, indented 0.4'' and full justified.
\end{quoting}

\emph{NOTE:} If you are using the electronic \LaTeX{} template to format your manuscript, the required spacing and formatting will be applied automatically.

\subsection{Headings}
The title of your paper should be typed in bold, 24-point type, with capital and lower-case letters, and centered at the top of the page. The names of the authors, business or academic affiliation, city, and state/province should follow on separate lines below the title. The names of authors with the same affiliation can be listed on the same line above their collective affiliation information. Author names are centered, and affiliations are centered and in italic type immediately below the author names. The affiliation line for each author is to include that author’s city, state, and zip/postal code (or city, province, zip/postal code and country, as appropriate). The first-page footnotes (lower left-hand side) contain the job title and department name, street address/mail stop, and AIAA member grade for each author. Author email addresses may be included also.

Major headings (``sections'' in the \LaTeX{} template commands) are bold 11-point font, centered, and numbered with Roman numerals.

Subheadings (``subsections'' in the \LaTeX{} template commands) are bold, flush left, and numbered with capital letters.

Sub-Subheadings (``subsubsections'' in the \LaTeX{} template commands) are italic, flush left, and numbered (1. 2. 3. etc.)

\subsection{Abstract}
The abstract should appear at the beginning of your paper. It should be one paragraph long (not an introduction) and complete in itself (no reference numbers). It should indicate subjects dealt with in the paper and state the objectives of the investigation. Newly observed facts and conclusions of the experiment or argument discussed in the paper must be stated in summary form; readers should not have to read the paper to understand the abstract. The abstract should be bold, indented 3 picas (1/2'') on each side, and separated from the rest of the document by blank lines above and below the abstract text..

\subsection{Nomenclature}
Papers with many symbols may benefit from a nomenclature list that defines all symbols with units, inserted between the abstract and the introduction. If one is used, it must contain all the symbology used in the manuscript, and the definitions should not be repeated in the text. In all cases, identify the symbols used if they are not widely recognized in the profession. Define acronyms in the text, not in the nomenclature.

\subsection{Footnotes and References}
Footnotes, where they appear, should be placed above the 1'' margin at the bottom of the page. To insert footnotes into the template, use the Insert>Footnote feature from the main menu as necessary. Numbered footnotes as formatted automatically in the template are acceptable, but superscript  symbols are the preferred AIAA style, *, $\dag$, $\ddag$, \S, \P, **, $\dag\dag$, $\ddag\ddag$, \S\S, etc.

List and number all references at the end of the paper. Corresponding bracketed numbers are used to cite references in the text \cite{vatistas1986reverse}, including citations that are an integral part of the sentence (e.g., ``It is shown in \cite{dornheim1996planetary} that\ldots '') or follow a mathematical expression: ``$A^{2} + B = C$ (Ref.~\cite{terster1997nasa}).'' For multiple citations, separate reference numbers with commas \cite{peyret2012computational,oates1997aerothermodynamics}, or use a dash to show a range \cite{volpe1994techniques,thompsonspacecraft,chi1993fluid,brandis2016nonequi}. Reference citations in the text should be in numerical order.

In the reference list, give all authors' names; do not use ``et al.''. Papers that have not been published should be cited as ``unpublished''; papers that have been submitted or accepted for publication should be cited as ``submitted for publication.'' Private communications and personal website should appear as footnotes rather than in the reference list.

References should be cited according to the standard publication reference style (for examples, see the ``References'' section of this template). Never edit titles in references to conform to AIAA style of spellings, abbreviations, etc. Names and locations of publishers should be listed; month and year should be included for reports and papers. For papers published in translation journals, please give the English citation first, followed by the original foreign language citation.

\subsection{Images, Figures and Tables}
All artwork, captions, figures, graphs, and tables will be reproduced exactly as submitted. Be sure to position any figures, tables, graphs, or pictures as you want them printed. AIAA will not be responsible for incorporating your figures, tables, etc. (Company logos and identification numbers are not permitted on your illustrations.)

Do not insert your tables and figures in text boxes. Figures should have no background, borders, or outlines. In the \LaTeX{} template, use the ``caption'' command to type caption text. Captions are bold with a single tab (no hyphen or other character) between the figure number and figure description.

% \begin{table}
% \caption{\label{tab:table1} Transitions selected for thermometry}
% \centering
% \begin{tabular}{lcccccc}
% \hline
% & Transition& & \multicolumn{2}{c}{}\\\cline{2-2}
% Line& $\nu''$& & $J'' $& Frequency, cm$^{-1}$& $FJ$, cm$^{-1}$& $G\nu $, cm$^{-1}$\\\hline
% a& 0& P$_{12}$& 2.5& 44069.416& 73.58& 948.66\\
% b& 1& R$_{2}$& 2.5& 42229.348& 73.41& 2824.76\\
% c& 2& R$_{21}$& 805& 40562.179& 71.37& 4672.68\\
% d& 0& R$_{2}$& 23.5& 42516.527& 1045.85& 948.76\\
% \hline
% \end{tabular}
% \end{table}

\begin{figure}[hbt!]
\centering
\includegraphics[width=.5\textwidth]{graph}
\caption{Magnetization as a function of applied fields.}
\end{figure}

Place figure captions below all figures; place table titles above the tables. If your figure has multiple parts, include the labels ``a),'' ``b),'' etc. below and to the left of each part, above the figure caption. Please verify that the figures and tables you mention in the text actually exist. \emph{Please do not include captions as part of the figures, and do not put captions in separate text boxes linked to the figures.} When citing a figure in the text, use the abbreviation ``Fig.'' except at the beginning of a sentence. Do not abbreviate ``Table.'' Number each different type of illustration (i.e., figures, tables, images) sequentially with relation to other illustrations of the same type.

Figure axis labels are often a source of confusion. Use words rather than symbols. As in the example to the right, write the quantity ``Magnetization'' rather than just ``M.'' Do not enclose units in parenthesis, but rather separate them from the preceding text by commas. Do not label axes only with units. As in Fig.~1, for example, write ``Magnetization, \si[per-mode=symbol]{\ampere\per\meter},'' not just ``A/m.'' Do not label axes with a ratio of quantities and units. For example, write ``Temperature, K,'' not ``Temperature/K.''

Multipliers can be especially confusing. Write ``Magnetization, \si[per-mode=symbol]{\kilo\ampere\per\meter}'' or ``Magnetization, \SI[per-mode=symbol]{e3}{\ampere\per\meter}.'' Do not write ``Magnetization (A/m) x 1000'' because the reader would not then know whether the top axis label in Fig.~1 meant 16000 A/m or 0.016 A/m. Figure labels must be legible, and all text within figures should be uniform in style and size, no smaller than 8-point type.

\subsection{Equations, Numbers, Symbols, and Abbreviations}
Equations are numbered consecutively, with equation numbers in parentheses flush right, as in Eq.~\eqref{sample:equation}. Insert a blank line above and below the equation. To insert an equation into the \LaTeX{} document, use the \verb|\begin{equation}...\end{equation}| command environment.

A sample equation is included here, formatted using the preceding instructions. To make your equation more compact, you can use the solidus (/), the exp function, or appropriate exponents. Use parentheses to avoid ambiguities in denominators.

\begin{equation}
\label{sample:equation}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}

Be sure that the symbols in your equation are defined before the equation appears, or immediately following. Italicize symbols ($T$ might refer to temperature, but T is the unit tesla). Refer to ``Eq.~(1),'' not ``(1)'' or ``equation (1)'' except at the beginning of a sentence: ``Equation (1) is\ldots'' Equations can be labeled other than ``Eq.'' should they represent inequalities, matrices, or boundary conditions. If what is represented is really more than one equation, the abbreviation ``Eqs.'' can be used.

Define abbreviations and acronyms the first time they are used in the text, even after they have already been defined in the abstract. Very common abbreviations such as AIAA, SI, ac, and dc do not have to be defined. Abbreviations that incorporate periods should not have spaces: write ``P.R.,'' not ``P.~R.'' Delete periods between initials if the abbreviation has three or more initials; e.g., U.N.~but ESA. Do not use abbreviations in the title unless they are unavoidable (for instance, ``AIAA'' in the title of this article).

\subsection{General Grammar and Preferred Usage}
Use only one space after periods or colons. Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Avoid dangling participles, such as, ``Using Eq.~(1), the potential was calculated.'' [It is not clear who or what used Eq.~(1).] Write instead ``The potential was calculated using Eq.~(1),'' or ``Using Eq.~(1), we calculated the potential.''

Insert a zero before decimal points: ``0.25,'' not ``.25.'' Use ``\si{\centi\meter\squared}'' not ``cc.'' Indicate sample dimensions as ``$\SI{0.1}{\centi\meter} \times \SI{0.2}{\centi\meter}$,'' not ``$0.1 \times \SI{0.2}{\centi\meter\squared}$.'' The preferred abbreviation for ``seconds'' is ``s,'' not ``sec.'' Do not mix complete spellings and abbreviations of units: use ``\si[per-mode=symbol]{\weber\per\meter\squared}'' or ``webers per square meter,'' not ``webers/m$^2$.'' When expressing a range of values, write ``7 to 9'' or ``7--9,'' not ``7$\sim$9.''

A parenthetical statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within parenthesis.) In American English, periods and commas are placed within quotation marks, like ``this period.'' Other punctuation is ``outside''! Avoid contractions; for example, write ``do not'' instead of ``don’t.'' The serial comma is preferred: ``A, B, and C'' instead of ``A, B and C.''

If you wish, you may write in the first person singular or plural and use the active voice (``I observed that\ldots'' or ``We observed that\ldots'' instead of ``It was observed that\ldots''). Remember to check spelling. If your native language is not English, please ask a native English-speaking colleague to proofread your paper.

Be aware of the different meanings of the homophones ``affect'' (usually a verb) and ``effect'' (usually a noun), ``complement'' and ``compliment,'' ``discreet'' and ``discrete,'' ``principal'' (e.g., ``principal investigator'') and ``principle'' (e.g., ``principle of measurement''). Do not confuse ``imply'' and ``infer.''

The word ``data'' is plural, not singular (i.e., ``data are,'' not ``data is''). The subscript for the permeability of vacuum $\mu_0$ is zero, not a lowercase letter ``o.'' The term for residual magnetization is ``remanence''; the adjective is ``remanent''; do not write ``remnance'' or ``remnant.'' The word ``micrometer'' is preferred over ``micron'' when spelling out this unit of measure. A graph within a graph is an ``inset,'' not an ``insert.'' The word ``alternatively'' is preferred to the word ``alternately'' (unless you really mean something that alternates). Use the word ``whereas'' instead of ``while'' (unless you are referring to simultaneous events). Do not use the word ``essentially'' to mean ``approximately'' or ``effectively.'' Do not use the word ``issue'' as a euphemism for ``problem.'' When compositions are not specified, separate chemical symbols by en-dashes; for example, ``NiMn'' indicates the intermetallic compound \ce{Ni_{0.5}Mn_{0.5}} whereas ``Ni--Mn'' indicates an alloy of some composition \ce{Ni_{x}Mn_{1-x}}.

Be aware of the different meanings of the homophones ``affect'' (usually a verb) and ``effect'' (usually a noun), ``complement'' and ``compliment,'' ``discreet'' and ``discrete,'' ``principal'' (e.g., ``principal investigator'') and ``principle'' (e.g., ``principle of measurement''). Do not confuse ``imply'' and ``infer.''

Prefixes such as ``non,'' ``sub,'' ``micro,'' ``multi,'' and ``"ultra'' are not independent words; they should be joined to the words they modify, usually without a hyphen. There is no period after the ``et'' in the abbreviation ``et al.'' The abbreviation ``i.e.,'' means ``that is,'' and the abbreviation ``e.g.,'' means ``for example'' (these abbreviations are not italicized).

\section{Conclusion}
A conclusion section is not required, though it is preferred. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions. \textit{Note that the conclusion section is the last section of the paper that should be numbered. The appendix (if present), acknowledgment, and references should be listed without numbers.}

\section*{Appendix}

An Appendix, if needed, should appear before the acknowledgments.

\section*{Acknowledgments}
An Acknowledgments section, if used, \textbf{immediately precedes} the References. Sponsorship information and funding data are included here. The preferred spelling of the word ``acknowledgment'' in American English is without the ``e'' after the ``g.'' Avoid expressions such as ``One of us (S.B.A.) would like to thank\ldots'' Instead, write ``F.~A.~Author thanks\ldots'' Sponsor and financial support acknowledgments are also to be listed in the ``acknowledgments'' section.

\bibliography{sample}

\end{document}

### 2022-11-28 research/manuscript-example/test.tex
Test LaTex file

\documentclass[conf]{new-aiaa}
%\documentclass[journal]{new-aiaa} for journal papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt}

\title{Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code approach}

\author{First A. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B. Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
\affil{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affil{Business or Academic Affiliation 2, City, State, Zip Code}

\begin{document}

\maketitle

\begin{abstract}
These instructions give you guidelines for preparing papers for AIAA Technical Papers using \LaTeX{}. Define all symbols used in the abstract. Do not cite references in the abstract. The footnote on the first page should list the Job Title and AIAA Member Grade for each author, if known Authors do not have to be AIAA members.
\end{abstract}

\section{Nomenclature}

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$A$  & amplitude of oscillation \\
$a$ &    cylinder diameter \\
$C_p$& pressure coefficient \\
$Cx$ & force coefficient in the \textit{x} direction \\
$Cy$ & force coefficient in the \textit{y} direction \\
c   & chord \\
d$t$ & time step \\
$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
$f, g$   & generic functions \\
$h$  & height \\
$i$  & time index during navigation \\
$j$  & waypoint index \\
$K$  & trailing-edge (TE) nondimensional angular deflection rate
\end{longtable*}}

\section{Introduction}
\lettrine{T}{his} document presents a Model-Based Systems Engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite:{architecting_spacecraft}.
For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University and Coast Guard Academy, the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite:{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation. Applying both an MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable.
This article presents the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software.

\section{CubeSats}

The CubeSat, originating from California Polytechnic State University in 1999, are a standardized form of nanosatellites.  Nanosatellites are satellites typically defined with a mass of less than 10 kg.  CubeSats, also known as Cube Satellites, are defined by standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 1.33 kg \cite:{cubesat_standard}.  These units can be stacked such as, for example, a 3-Unit (3U) CubeSat with standard dimensions of 10 cm x 10 cm x 34.05 cm ± 0.03 cm and a maximum mass of 4.00 kg \cite:{cubesat_standard}.

CubeSats were initially conceived as educational tools for space systems engineering \cite:{3A}.  Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these satellites.  As such, there has been increasing popularity for CubeSats ass seen by the number of launches in figure X since year 2000 \cite:{2A}.

University groups especially are a large contributor in the overall number of launches of CubeSats yearly.  As of July 17, 2021, alone, there have been 68 CubeSat launches with 40 of them being from university groups (about 58 percent of launches) and university groups have consistently maintained plurality on total launches \cite:{2A}.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{figure1}
    \caption{Nanosatellite launch data provided by M. Swartwout \cite:{2A}}
    \end{figure}
\section{CubeSats}

\subsection{What is SeaLion}
The SeaLion mission is a collaborative mission between Old Dominion University (ODU), the United Stated Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT) to design and produce a 3U CubeSat.

SeaLion consists of three payloads for on-orbit validation.  ODU provided one payload while the USCGA and AFIT provided the other two payloads.  SeaLion is planned to fly as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF), currently scheduled for March, 2023 \cite:{sealion_cdr}.

\section{Model-Based Systems Engineering}
Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite:{architecting_spacecraft}.  However, these documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite:{ibm_mbse}.  Models provide the following key advantages over document-based approaches \cite:{ibm_mbse,value_and_benefits_mbse}:

\begin{enumerate}
\item Information is readily communicated and shared within the project

\item Changes are easily accommodated

\item Traceability is automated
\end{enumerate}

\subsection{Why Create a Modelling Language}

A common issue regarding tools for both students and amateur developers for system engineering is that many of the tools are proprietary and thus, unavailable to many potential users without significant cost burden \cite:{??}.  Thus, the goal of the Mach30 modeling language (m30ml), described herein, was to create an open-source tool that is readily available to anyone who wishes to model their respective systems while also making it easily learnable.

\section{Mach30 Modelling Language}

The SeaLion Architecture uses m30ml to specify references, stakeholder needs, user stories, & data structures for facilitating traceability of design decisions within the Mission ConOps \cite:{mach30_git}.  The SeaLion repository is also structured as a Distributed OSHW Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.

This is all done in an effort to execute the project via a documentation as code philosophy. A philosophy in which documentation is written with the same tools as code \cite:{docs_as_code}. This allows for workflows between development teams to be more closely integrated.

\end{document}

### 2022-11-30 research/manuscript-example/manuscript.tex
Start draft to manuscript and associated references

--- 2022-11-28 research/manuscript-example/test.tex
@@
 \begin{abstract}
-These instructions give you guidelines for preparing papers for AIAA Technical Papers using \LaTeX{}.
-Define all symbols used in the abstract.
-Do not cite references in the abstract.
-The footnote on the first page should list the Job Title and AIAA Member Grade for each author, if known Authors do not have to be AIAA members.
+PLACEHOLDER
 \end{abstract}
@@
 \section{Introduction}
-\lettrine{T}{his} document presents a Model-Based Systems Engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite:{architecting_spacecraft}.
+\lettrine{T}{his} article presents the Mach30 modeling language (m30ml), tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software.
+
+The m30ml was created based on a model-based systems engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite:{architecting_spacecraft}.
+
 For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University and Coast Guard Academy, the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite:{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
 Applying both an MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable.
-This article presents the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software.
+
+\section{SeaLion Mission}
+
+The SeaLion mission is a collaborative mission between Old Dominion University (ODU), the United Stated Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT) to design and produce a 3-Unit (3U) CubeSat.
+
+SeaLion consists of three payloads for on-orbit validation.
+ODU provided one payload while the USCGA and AFIT provided the other two payloads.
+SeaLion is planned to fly as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF), currently scheduled for March, 2023 \cite:{sealion_cdr}.
 
@@
 CubeSats, also known as Cube Satellites, are defined by standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 1.33 kg \cite:{cubesat_standard}.
-These units can be stacked such as, for example, a 3-Unit (3U) CubeSat with standard dimensions of 10 cm x 10 cm x 34.05 cm ± 0.03 cm and a maximum mass of 4.00 kg \cite:{cubesat_standard}.
+These units can be stacked such as, for example, a 3U CubeSat with standard dimensions of 10 cm X 10 cm X 34.05 cm +/- 0.03 cm and a maximum mass of 4.00 kg \cite:{cubesat_standard}.
 
-CubeSats were initially conceived as educational tools for space systems engineering \cite:{3A}.
+\subsection{CubeSat Users}
+
+CubeSats were initially conceived as educational tools for space systems engineering \cite:{heidt_new}.
 Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these satellites.
-As such, there has been increasing popularity for CubeSats ass seen by the number of launches in figure X since year 2000 \cite:{2A}.
+As such, there has been increasing popularity for CubeSats ass seen by the number of launches in \ref{swartwout_data_graph} since year 2000 \cite:{swartwout_data}.
 
-University groups especially are a large contributor in the overall number of launches of CubeSats yearly.
-As of July 17, 2021, alone, there have been 68 CubeSat launches with 40 of them being from university groups (about 58 percent of launches) and university groups have consistently maintained plurality on total launches \cite:{2A}.
+University groups especially are a large contributor in the overall number of launches of CubeSats yearly with university groups consistently maintaining plurality on total launches \cite:{swartwout_data}.
+Thus, a need for readily available and easily learnable tools for students especially exists for those who are new to both CubeSat design and systems engineering.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figure1}
-    \caption{Nanosatellite launch data provided by M. Swartwout \cite:{2A}}
+    \includegraphics[width=.5\textwidth]{swartwout_data_graph}
+    \caption{Nanosatellite launch data provided by M. Swartwout \cite:{swartwout_data}.}
+    \label{swartwout_data_graph}
 \end{figure}
-\section{CubeSats}
 
-\subsection{What is SeaLion}
-The SeaLion mission is a collaborative mission between Old Dominion University (ODU), the United Stated Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT) to design and produce a 3U CubeSat.
+\section{Goals}
 
-SeaLion consists of three payloads for on-orbit validation.
-ODU provided one payload while the USCGA and AFIT provided the other two payloads.
-SeaLion is planned to fly as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF), currently scheduled for March, 2023 \cite:{sealion_cdr}.
+The goal of the SeaLion CubeSat flight software architecture was to capture the data structures and expected behaviors of the flight software, such that it can be unambiguiously understood enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite:{sealion_mission_architecture}.
 
-\section{Model-Based Systems Engineering}
+The MBSE approach was of interest to the SeaLion CubeSat flight software team, as to yield the benefits of reducing ambiguity that usually comes with using informal language for specifying aspects of a system, as well as minimizing duplication of content that tends to accumulate in a document-based systems engineering approach.
+
+Selection of a modeling language, modeling tool, and technical approach needs to be taken into consideration, in order to properly adopt a MBSE approach.
+The m30ml MBSE approach uses the Docs as Code and the Ontological Modeling Language (OML) as its basis of design.
+
+Other considerations include overhead incurred with training the team, as well as technical overhead with setting up and maintaining the modeling tools.
+
+\subsection{Model-Based Systems Engineering}
+
 Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite:{architecting_spacecraft}.
 However, these documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite:{ibm_mbse}.
-Models provide the following key advantages over document-based approaches \cite:{ibm_mbse,value_and_benefits_mbse}:
+Models provide the following key advantages over document-based approaches \cite:{ibm_mbse}:
 
 \begin{enumerate}
-\item Information is readily communicated and shared within the project
+\item Information is readily communicated and shared within the project \cite:{ibm_mbse}.
 
-\item Changes are easily accommodated
+\item Changes are easily accommodated \cite:{ibm_mbse}.
 
-\item Traceability is automated
+\item Traceability is automated \cite:{ibm_mbse}.
+
+\item PLACEHOLDER
 \end{enumerate}
 
-\subsection{Why Create a Modelling Language}
+The m30ml MBSE approach uses the Docs as Code and the Ontological Modeling Language (OML) as its basis of design.
 
-A common issue regarding tools for both students and amateur developers for system engineering is that many of the tools are proprietary and thus, unavailable to many potential users without significant cost burden \cite:{??}.
-Thus, the goal of the Mach30 modeling language (m30ml), described herein, was to create an open-source tool that is readily available to anyone who wishes to model their respective systems while also making it easily learnable.
+\subsection{Docs As Code Approach}
+
+Documentation as Code, or also known as Docs as Code, refers to a philosophy that you should be writing documentation with the same tools as code \cite:{docs_as_code}.
+These tools may include version control (e.g., Git), issue trackers, code tools, etc.
+
+\begin{quoting}
+    This means following the same workflows as development teams, and being integrated in the product team.
+It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible \cite:{docs_as_code}.
+\end{quoting}
+
+It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same tools used to manage code, using version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite:{docs_as_code}.
+
+\subsection{Ontological Modeling Language}
+
+PLACEHOLDER
 
@@
 
+\subsection{Modeling Language, Tool, & Methodology}
+
+The Mach30 modeling language (m30ml) is a YAML-based modeling language for defining a software architecture.
+Since YAML is a lightweight, highly-structured, human-readable, machine queryable, and line-oriented markup language, it was ideal for document generation use cases, as well as use with version control tools like Git.
+
+Mach30 also had minimal technical overhead as it was compatible with modern doc tools such as asciidoctor & bibtex.
+
+Mach30 also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, and data structures, with relationship elements for defining traceability between modeling elements.
+
+For the aforementioned reasons, the SeaLion CubeSat flight software team downselected m30ml for specifying the SeaLion CubeSat flight software architecture \cite:{mach30_git}.
+
+\subsection{Stakeholder Needs}
+
+The SeaLion project's methodology documentation uses m30ml based on YAML architecture modeling tools.
+The first step to build the architecture is to define the stakeholder needs.
+The two stakeholders for Sealion are ODU and CGA with their respective needs categorized on priority from primary to secondary to tertiary.
+These stakeholder needs are listed in the following Table PLACEHOLDER.
+
+PLACEHOLDER TABLE
+
+\subsection{User Stories}
+
+The SeaLion Mission Architecture's stakeholder needs are then used to identify a series of user stories which then lead to design decisions captured in data structure and activity definitions.
+These are created from the perspective of the ground station operator to define the tasks that need to be completed to satisfy the user stories.
+These user stories are listed in the following Table PLACEHOLDER.
+
+PLACEHOLDER TABLE
+
+\subsection{Example Data Structure}
+
+An example data structure can be derived from user stories as presented in Table PLACEHOLDER.
+
+PLACEHOLDER TABLE
+
+\section{Future Work}
+
+PLACEHOLDER
+
+\section{Conclusion}
+
+PLACEHOLDER
+
+\section*{Acknowledgments}
+An Acknowledgments section, if used, \textbf{immediately precedes} the References.
+Sponsorship information and funding data are included here.
+The preferred spelling of the word ``acknowledgment'' in American English is without the ``e'' after the ``g.'' Avoid expressions such as ``One of us (S.B.A.) would like to thank\ldots'' Instead, write ``F.~A.~Author thanks\ldots'' Sponsor and financial support acknowledgments are also to be listed in the ``acknowledgments'' section.
+
+\bibliography{manuscript_references}
+
 \end{document}

### 2022-12-01 research/manuscript-example/manuscript.tex
Add more detail to goals. Add nomenclature list.

@@
 \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
-$A$  & amplitude of oscillation \\
-$a$ &    cylinder diameter \\
-$C_p$& pressure coefficient \\
-$Cx$ & force coefficient in the \textit{x} direction \\
-$Cy$ & force coefficient in the \textit{y} direction \\
-c   & chord \\
-d$t$ & time step \\
-$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
-$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
-$f, g$   & generic functions \\
-$h$  & height \\
-$i$  & time index during navigation \\
-$j$  & waypoint index \\
-$K$  & trailing-edge (TE) nondimensional angular deflection rate
+$1U$ 1-Unit \\
+$3U$ 3-Unit \\
+$BOM$  & Bill of Materials \\
+$ConOps$  & Concept of Operations \\
+$DOF$  & Distributed OSHW Framework  \\
+$m30ml$  & mach30 modeling language \\
+$MBSE$ &    model-based systems engineering  \\
+$ODU$& Old Dominion University \\
+$OML$  & Ontological Modeling Language \\
+$OSHW$ & Open Source Hardware \\
+$USCGA$ & United Stated Coast Guard Academy \\
+$WFF$   & Wallops Flight Facility  
 \end{longtable*}}
@@
 
-For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University and Coast Guard Academy, the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite:{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
+For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University (ODU), Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT), the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite:{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
 Applying both an MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable.
@@
 
-The SeaLion mission is a collaborative mission between Old Dominion University (ODU), the United Stated Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT) to design and produce a 3-Unit (3U) CubeSat.
+The SeaLion mission is a collaborative mission between ODU, USCGA, and the AFIT to design and produce a 3-Unit (3U) CubeSat.
 
@@
 
+To achieve these goals m30ml should be able to perform the following:
+
+\begin{itemize}
+    \item Documents (both for mission and flight architecture) should be able to persist on a local system.
+
+    \item Documents should be in plaintext as to be compatible with modern distributed version control system (e.g., git) and for ease of use.
+
+    \item Documents should be able to sit alongside code and speak to one another.
+
+    \item Documents should be model-based as to have a separation of concerns between content and formatting as well as be both human and machine-readable for querying and generating views.
+\end{itemize}
+
 \subsection{Model-Based Systems Engineering}
@@
 
-\begin{enumerate}
+\begin{itemize}
     \item Information is readily communicated and shared within the project \cite:{ibm_mbse}.
@@
     \item PLACEHOLDER
-\end{enumerate}
+\end{itemize}
 

### 2022-12-02 research/manuscript-example/manuscript.tex
Additional edits and additional figure

@@
 Selection of a modeling language, modeling tool, and technical approach needs to be taken into consideration, in order to properly adopt a MBSE approach.
-The m30ml MBSE approach uses the Docs as Code and the Ontological Modeling Language (OML) as its basis of design.
+The m30ml MBSE approach uses the documentation as code, or also know as docs-as-code, approach and the Ontological Modeling Language (OML) as its basis of design.
 
@@
 \begin{itemize}
-    \item Information is readily communicated and shared within the project \cite:{ibm_mbse}.
+    \item Information is readily communicated and shared within the project.
 
-    \item Changes are easily accommodated \cite:{ibm_mbse}.
+    \item Changes are easily accommodated.
 
-    \item Traceability is automated \cite:{ibm_mbse}.
-
-    \item PLACEHOLDER
+    \item Traceability is automated.
 \end{itemize}
 
-The m30ml MBSE approach uses the Docs as Code and the Ontological Modeling Language (OML) as its basis of design.
+As mentioned prior, the m30ml MBSE approach uses the docs-as-code, approach and OML as its basis of design.
 
@@
 
-Documentation as Code, or also known as Docs as Code, refers to a philosophy that you should be writing documentation with the same tools as code \cite:{docs_as_code}.
+Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite:{docs_as_code}.
 These tools may include version control (e.g., Git), issue trackers, code tools, etc.
@@
 The SeaLion Architecture uses m30ml to specify references, stakeholder needs, user stories, & data structures for facilitating traceability of design decisions within the Mission ConOps \cite:{mach30_git}.
-The SeaLion repository is also structured as a Distributed OSHW Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
+The SeaLion repository is also structured as a Distributed Open Source Hardware (OSHW) Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
 
@@
 
-The Mach30 modeling language (m30ml) is a YAML-based modeling language for defining a software architecture.
+The m30ml is a YAML-based modeling language for defining a software architecture.
 Since YAML is a lightweight, highly-structured, human-readable, machine queryable, and line-oriented markup language, it was ideal for document generation use cases, as well as use with version control tools like Git.
+The following \ref{user_story} showcases the simplicity of the YAML file.
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=.5\textwidth]{ping_satellite}
+    \caption{An example YAML file for a user story.}
+    \label{user_story}
+\end{figure}
 
@@
 
+\subsection{File Structure and Generation}
+
+The m30ml file structure for architecture is simple and easy to use.
+Architecture is split into the four folders of references, stakeholder needs, user stories, and datastructures.
+Datastructures are derived from user stories which are subsequently derived from stakeholder needs with their respective references.
+The continued link between their respective YAML files allows for continous path from which documents can be updated.
+
+The following PLACEHOLDER TABLE, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the m30ml structure and injected directly into this article.
+Should any changes be made to the SeaLion architecture repository, the tables can be immediately regenerated for continous updates.
+
 \subsection{Stakeholder Needs}
@@
 The first step to build the architecture is to define the stakeholder needs.
-The two stakeholders for Sealion are ODU and CGA with their respective needs categorized on priority from primary to secondary to tertiary.
+The two primary stakeholders for Sealion are ODU and CGA with their respective needs categorized on priority from primary to secondary to tertiary.
 These stakeholder needs are listed in the following Table PLACEHOLDER.

### 2022-12-03 research/manuscript-example/manuscript.tex
Added OML references and paragraph

@@
 
-\author{First A.
-Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B.
-Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
-\affil{Business or Academic Affiliation 1, City, State, Zip Code}
-\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
-\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
-\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
-\affil{Business or Academic Affiliation 2, City, State, Zip Code}
+\author{Sean Marquez and Kevin Chiu}
+\affil{Old Dominion University, Norfolk, VA, 23529}
+\author{Sharan Asundi, Ph.D. \\footnote{Assistant Professor, Department of Mechanical & Aerospace Engineering, Old Dominion University}}
+\affil{Old Dominion University, Norfolk, VA, 23529}
 
@@
 $OSHW$ & Open Source Hardware \\
+$OWL2$ & Web Ontology Language 2 \\
+$SWRL$ & Semantic Web Rule Language \\
 $USCGA$ & United Stated Coast Guard Academy \\
@@
 
-PLACEHOLDER
+OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite:{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite:{oml_language}.
+OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite:{oml_origin_and_rationale}.
+Thus, OML served as a useful basis to create the m30ml since both run on similar philosophies to simplify usage for the end user.
 

### 2022-12-03 research/manuscript-example/manuscript.tex
fix cite syntax in manuscript.tex

@@
 
-The m30ml was created based on a model-based systems engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite:{architecting_spacecraft}.
+The m30ml was created based on a model-based systems engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite{architecting_spacecraft}.
 
-For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University (ODU), Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT), the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite:{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
+For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University (ODU), Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT), the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
 Applying both an MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable.
@@
 ODU provided one payload while the USCGA and AFIT provided the other two payloads.
-SeaLion is planned to fly as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF), currently scheduled for March, 2023 \cite:{sealion_cdr}.
+SeaLion is planned to fly as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF), currently scheduled for March, 2023 \cite{sealion_cdr}.
 
@@
 Nanosatellites are satellites typically defined with a mass of less than 10 kg.
-CubeSats, also known as Cube Satellites, are defined by standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 1.33 kg \cite:{cubesat_standard}.
-These units can be stacked such as, for example, a 3U CubeSat with standard dimensions of 10 cm X 10 cm X 34.05 cm +/- 0.03 cm and a maximum mass of 4.00 kg \cite:{cubesat_standard}.
+CubeSats, also known as Cube Satellites, are defined by standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 1.33 kg \cite{cubesat_standard}.
+These units can be stacked such as, for example, a 3U CubeSat with standard dimensions of 10 cm X 10 cm X 34.05 cm +/- 0.03 cm and a maximum mass of 4.00 kg \cite{cubesat_standard}.
 
@@
 
-CubeSats were initially conceived as educational tools for space systems engineering \cite:{heidt_new}.
+CubeSats were initially conceived as educational tools for space systems engineering \cite{heidt_new}.
 Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these satellites.
-As such, there has been increasing popularity for CubeSats ass seen by the number of launches in \ref{swartwout_data_graph} since year 2000 \cite:{swartwout_data}.
+As such, there has been increasing popularity for CubeSats ass seen by the number of launches in \ref{swartwout_data_graph} since year 2000 \cite{swartwout_data}.
 
-University groups especially are a large contributor in the overall number of launches of CubeSats yearly with university groups consistently maintaining plurality on total launches \cite:{swartwout_data}.
+University groups especially are a large contributor in the overall number of launches of CubeSats yearly with university groups consistently maintaining plurality on total launches \cite{swartwout_data}.
 Thus, a need for readily available and easily learnable tools for students especially exists for those who are new to both CubeSat design and systems engineering.
@@
     \includegraphics[width=.5\textwidth]{swartwout_data_graph}
-    \caption{Nanosatellite launch data provided by M. Swartwout \cite:{swartwout_data}.}
+    \caption{Nanosatellite launch data provided by M. Swartwout \cite{swartwout_data}.}
     \label{swartwout_data_graph}
@@
 
-The goal of the SeaLion CubeSat flight software architecture was to capture the data structures and expected behaviors of the flight software, such that it can be unambiguiously understood enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite:{sealion_mission_architecture}.
+The goal of the SeaLion CubeSat flight software architecture was to capture the data structures and expected behaviors of the flight software, such that it can be unambiguiously understood enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.
 
@@
 
-Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite:{architecting_spacecraft}.
-However, these documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite:{ibm_mbse}.
-Models provide the following key advantages over document-based approaches \cite:{ibm_mbse}:
+Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.
+However, these documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.
+Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:
 
@@
 
-Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite:{docs_as_code}.
+Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite{docs_as_code}.
 These tools may include version control (e.g., Git), issue trackers, code tools, etc.
@@
     This means following the same workflows as development teams, and being integrated in the product team.
-It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible \cite:{docs_as_code}.
+It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible \cite{docs_as_code}.
 \end{quoting}
 
-It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same tools used to manage code, using version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite:{docs_as_code}.
+It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same tools used to manage code, using version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite{docs_as_code}.
 
@@
 
-OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite:{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite:{oml_language}.
-OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite:{oml_origin_and_rationale}.
+OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite{oml_language}.
+OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.
 Thus, OML served as a useful basis to create the m30ml since both run on similar philosophies to simplify usage for the end user.
@@
 
-The SeaLion Architecture uses m30ml to specify references, stakeholder needs, user stories, & data structures for facilitating traceability of design decisions within the Mission ConOps \cite:{mach30_git}.
+The SeaLion Architecture uses m30ml to specify references, stakeholder needs, user stories, & data structures for facilitating traceability of design decisions within the Mission ConOps \cite{mach30_git}.
 The SeaLion repository is also structured as a Distributed Open Source Hardware (OSHW) Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
@@
 This is all done in an effort to execute the project via a documentation as code philosophy.
-A philosophy in which documentation is written with the same tools as code \cite:{docs_as_code}.
+A philosophy in which documentation is written with the same tools as code \cite{docs_as_code}.
 This allows for workflows between development teams to be more closely integrated.
@@
 
-For the aforementioned reasons, the SeaLion CubeSat flight software team downselected m30ml for specifying the SeaLion CubeSat flight software architecture \cite:{mach30_git}.
+For the aforementioned reasons, the SeaLion CubeSat flight software team downselected m30ml for specifying the SeaLion CubeSat flight software architecture \cite{mach30_git}.
 

### 2022-12-05 buildDocs.sh
generate example LaTeX manuscript from model

@@ -1,112 +1,186 @@
 #!/usr/bin/env bash
 
-# Install node_modules, if not already installed
-if [ ! -r ./node_modules ]; then
-    echo "Installing node_modules..."
-    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'npm ci'
+## Install node_modules, if not already installed
+#if [ ! -r ./node_modules ]; then
+#    echo "Installing node_modules..."
+#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'npm ci'
+#fi
+#
+## Install m30mlTools/node_modules, if not already installed
+#if [ ! -r ./m30mlTools/node_modules ]; then
+#    echo "Installing m30mlTools/node_modules..."
+#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd m30mlTools && npm ci'
+#fi
+#
+## Install dof-helpers/node_modules, if not already installed
+#if [ ! -r ./dof-helpers/node_modules ]; then
+#    echo "Installing dof-helpers/node_modules..."
+#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd dof-helpers && npm ci'
+#fi
+#
+## Create dist/ directory, if none exists
+#if [ ! -r ./dist ]; then
+#    echo "Creating dist/ directory..."
+#    mkdir dist/
+#fi
+#
+## copy operating-mode-as-fsm.puml to dist/...
+#echo "copying operating-mode-as-fsm.puml to dist/..."
+#docker run --rm -v $PWD:/src -w /src node bash -c 'cp ./components/sealion-cubesat/components/sealion-obc/components/dilophos/fsw-architecture/operating-mode-as-fsm.puml dist/'
+#
+## generate dist/component.yaml & symlink to architecture/ directory
+#echo "generating dist/component.yaml & symlink to architecture/ directory..."
+#docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'node dof-helpers/parseComponent.js && mkdir architecture/4-Components && ln -srv dist/component.yaml architecture/4-Components'
+#
+## Build the unified model
+#echo "Building the unified model..."
+#docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'node m30mlTools/buildUnifiedModel.js && cp dist/architecture.yaml dist/architecture.yml'
+#
+## generate stakeholder needs mapping
+#echo "generating stakeholder needs mapping..."
[…]

### 2022-12-05 buildDocs.sh
Fix stupid LaTeX/BibTeX to PDF pipeline

@@ -147,40 +147,15 @@ echo "Copy LaTeX files and assets (required for generating PDF document) to dist
 
 cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls assets/*
 
-## https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
-#cmd="pdflatex manuscript-example.tex"
-#dockercmd="docker run --rm -v $PWD/dist:/srv -w /srv embix/pdflatex:latest $cmd"
-#condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
-#
-#if ! eval $condition; then
-#    echo "Generating PDF document from LaTeX document of manuscript via docker..."
-#    eval $(echo $dockercmd)
-#else
-#    echo "Generating PDF document from LaTeX document of manuscript..."
-#    eval $cmd
-#fi
-#
-#cmd="bibtex new-aiaa.aux"
-#dockercmd="docker run --rm -v $PWD/dist:/srv -w /srv embix/bibtex:latest $cmd"
-#condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
-#
-#if ! eval $condition; then
-#    echo "Generating PDF document from LaTeX document of manuscript via docker..."
-#    eval $(echo $dockercmd)
-#else
-#    echo "Generating PDF document from LaTeX document of manuscript..."
-#    eval $cmd
-#fi
-#
-#cmd="pdflatex manuscript-example.tex && pdflatex manuscript-example.tex"
-#dockercmd="docker run --rm -v $PWD/dist:/srv -w /srv embix/pdflatex:latest $cmd"
-#condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
-#
-#if ! eval $condition; then
-#    echo "Generating PDF document from LaTeX document of manuscript via docker..."
-#    eval $(echo $dockercmd)
-#else
-#    echo "Generating PDF document from LaTeX document of manuscript..."
-#    eval $cmd
-#fi
+# https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
+cmd="pdflatex manuscript-example.tex && bibtex manuscript-example.aux && pdflatex manuscript-example.tex && pdflatex manuscript-example.tex"
[…]

### 2022-12-05 buildDocs.sh
update build script to build manuscript.yaml

@@ -111,7 +111,7 @@
 #echo "generating abstract.pdf..."
 #docker run --rm --volume $PWD:/src -w "/src" asciidoctor/docker-asciidoctor asciidoctor research/abstract.adoc -o dist/abstract.pdf -r asciidoctor-pdf -r asciidoctor-diagram -r asciidoctor-bibtex -b pdf
 
-#### generate manuscript ####
+#### generate example manuscript ####
 # for linkml docker command usage, see https://hub.docker.com/r/linkml/linkml
 
 clitool="linkml-validate"
@@ -149,6 +149,55 @@ cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls 
 
 # https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
 cmd="pdflatex manuscript-example.tex && bibtex manuscript-example.aux && pdflatex manuscript-example.tex && pdflatex manuscript-example.tex"
+dockercmd="docker run --rm -v $PWD/dist:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
+condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
+
+if ! eval $condition; then
+    echo "Generating PDF document from LaTeX document of manuscript via docker..."
+    eval $(echo $dockercmd)
+else
+    echo "Generating PDF document from LaTeX document of manuscript..."
+    eval $cmd
+fi
+
+#### generate manuscript ####
+# for linkml docker command usage, see https://hub.docker.com/r/linkml/linkml
+
+clitool="linkml-validate"
+cmdargs="-s manuscript-metamodel.yaml manuscript.yaml"
+cmd="$clitool $cmdargs"
+dockercmd="docker run --rm -v $PWD/manuscript:/work -w /work linkml/linkml:1.3.14 $cmd"
+condition="$clitool --help | grep 'Validates instance data' > /dev/null"
+
+if ! eval $condition; then
+    echo "Validating linkml model of example manuscript via docker..."
+    eval $(echo $dockercmd)
+else
+    echo "Validating linkml model of example manuscript..."
+    eval $cmd
+fi
+
+clitool="jinja2"
+cmdargs="-o dist/manuscript.tex --format yaml templates/manuscript.tex.jinja2 manuscript/manuscript.yaml"
[…]

### 2022-12-06 research/manuscript-example/manuscript.tex

@@
 \affil{Old Dominion University, Norfolk, VA, 23529}
-\author{Sharan Asundi, Ph.D. \\footnote{Assistant Professor, Department of Mechanical & Aerospace Engineering, Old Dominion University}}
+\author{Sharan Asundi, Ph.D. \footnote{Assistant Professor, Department of Mechanical & Aerospace Engineering, Old Dominion University}}
 \affil{Old Dominion University, Norfolk, VA, 23529}
@@
 \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
-$1U$ 1-Unit \\
-$3U$ 3-Unit \\
+$1U$ & 1-Unit \\
+$3U$ & 3-Unit \\
 $BOM$  & Bill of Materials \\
@@
 $DOF$  & Distributed OSHW Framework  \\
-$m30ml$  & mach30 modeling language \\
-$MBSE$ &    model-based systems engineering  \\
-$ODU$& Old Dominion University \\
+$M30ML$  & Mach30 Modeling Language \\
+$MBSE$ & Model-Based Systems Engineering  \\
+$ODU$ & Old Dominion University \\
 $OML$  & Ontological Modeling Language \\
@@
 \section{Introduction}
-\lettrine{T}{his} article presents the Mach30 modeling language (m30ml), tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software.
+\lettrine{T}{his} article presents the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software using a model-based approach.
 
-The m30ml was created based on a model-based systems engineering (MBSE) approach to systems engineering whereby models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite{architecting_spacecraft}.
+A model-based systems engineering (MBSE) approach to systems engineering is where models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite{architecting_spacecraft}.
+The NASA handbook on systems engineering can be applied to CubeSat Mission design, in effort to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture cite{asundi13_cubes}.
 
-For the SeaLion Mission, a joint CubeSat mission between the Old Dominion University (ODU), Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT), the flight software team adopted an MBSE approach to flight software architecture, using a docs-as-code approach \cite{docs_as_code}, whereby the same tools and methodologies for managing software are also used for configuration management of documentation.
-Applying both an MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable.
+For the SeaLion Mission, the flight software team adopted an MBSE approach to flight software architecture using a document as code, also known as docs-as-code, approach \cite{docs_as_code}.
+This approach is where the same tools and methodologies for managing software are also used for configuration management of documentation.
+Applying both a MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable while minimizing configuration management overhead.
+A docs-as-code toolchain is also a file-based approach that allows for models to be persistent on local file systems without the additional use of cloud-based software or services.
 
@@
 
-The SeaLion mission is a collaborative mission between ODU, USCGA, and the AFIT to design and produce a 3-Unit (3U) CubeSat.
+The SeaLion mission is a a joint CubeSat mission between the Old Dominion University (ODU), Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT) to design and produce a 3-Unit (3U) CubeSat.
 
@@
 
-\section{CubeSats}
+\subsection{CubeSats}
 
@@
 Nanosatellites are satellites typically defined with a mass of less than 10 kg.
-CubeSats, also known as Cube Satellites, are defined by standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 1.33 kg \cite{cubesat_standard}.
-These units can be stacked such as, for example, a 3U CubeSat with standard dimensions of 10 cm X 10 cm X 34.05 cm +/- 0.03 cm and a maximum mass of 4.00 kg \cite{cubesat_standard}.
+CubeSats, also known as Cube Satellites, are defined by a standardized and modular architecture of 1-Unit (1U) cubes with dimensions of 10 cm X 10 cm X 10 cm with a maximum mass of 2.00 kg \cite{cds_rev14}.
+These units can be expanded upon such as, for example, a 3U CubeSat with standard dimensions of 10 cm X 10 cm X 34.05 cm and a maximum mass of 6.00 kg \cite{cds_rev14}.
 
@@
 CubeSats were initially conceived as educational tools for space systems engineering \cite{heidt_new}.
-Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these satellites.
-As such, there has been increasing popularity for CubeSats ass seen by the number of launches in \ref{swartwout_data_graph} since year 2000 \cite{swartwout_data}.
+Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research, that were previous monopolized by much larger satellites, due to the low cost of production and launch of these satellites.
+As such, there has been increasing popularity for CubeSats as seen by the increasing number of launches in \ref{swartwout_data_graph} since inception \cite{swartwout_data}.
 
 University groups especially are a large contributor in the overall number of launches of CubeSats yearly with university groups consistently maintaining plurality on total launches \cite{swartwout_data}.
-Thus, a need for readily available and easily learnable tools for students especially exists for those who are new to both CubeSat design and systems engineering.
+Thus, a need for readily available and easily learnable system engineering approachs and tools, for students especially, exists for those who are new to either CubeSat design and systems engineering.
 
@@
 
-The goal of the SeaLion CubeSat flight software architecture was to capture the data structures and expected behaviors of the flight software, such that it can be unambiguiously understood enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.
-
+The goal of the SeaLion CubeSat flight software architecture was to capture the data structures and expected behaviors of the flight software, such that it can be unambiguiously understood well enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.
 The MBSE approach was of interest to the SeaLion CubeSat flight software team, as to yield the benefits of reducing ambiguity that usually comes with using informal language for specifying aspects of a system, as well as minimizing duplication of content that tends to accumulate in a document-based systems engineering approach.
 
-Selection of a modeling language, modeling tool, and technical approach needs to be taken into consideration, in order to properly adopt a MBSE approach.
-The m30ml MBSE approach uses the documentation as code, or also know as docs-as-code, approach and the Ontological Modeling Language (OML) as its basis of design.
+The final approach had to achieve the following goals:
+\begin{itemize}
+    \item Ensure templates only contain formatting data (this includes not storing boilerplate text in templates)
 
-Other considerations include overhead incurred with training the team, as well as technical overhead with setting up and maintaining the modeling tools.
+    \item Ensure models are the authoritative source of truth for all artifact content (e.g. artifact structure, meta-data, boilerplate, commentary, discussion, diagrams, tables, etc.)
 
-To achieve these goals m30ml should be able to perform the following:
+    \item Models should persist on the local filesystem
 
-\begin{itemize}
-    \item Documents (both for mission and flight architecture) should be able to persist on a local system.
-
-    \item Documents should be in plaintext as to be compatible with modern distributed version control system (e.g., git) and for ease of use.
+    \item Documents should be in plaintext as to be compatible with modern distributed version control system (e.g., Git) and for ease of use.
 
@@
 
+Selection of a modeling language and modeling tool was taken into consideration in order to properly adopt a MBSE approach.
+Other considerations include overhead incurred with training the team, as well as technical overhead with setting up and maintaining the modeling tools.
+The flight software team also decided to adopt a docs-as-code approach to further enhance a MBSE approach to achieve the listed goals.
+
 \subsection{Model-Based Systems Engineering}
@@
 Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.
-However, these documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.
+Information in a traditional systems engineering approach today is mostly captured informally, not authored based on a methodology, configuration managed in silo tools, adhocly and infrequently integrated, not easily traceable to its provenance, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.
+These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.
+
+In contrast, a model-based systems engineering approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.
 Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:
@@
 \end{itemize}
-
-As mentioned prior, the m30ml MBSE approach uses the docs-as-code, approach and OML as its basis of design.
 
@@
 It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same tools used to manage code, using version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite{docs_as_code}.
+It also allows for models to be persistent on a local file system without use of cloud-based services or software.
+
+\section{Mach30 Modelling Language}
+
+The flight software team conducted a trade study to downselect a suitable modeling language for the afformentioned goals.
+The languages considered with SysML V1, SysML V2, PlantUML, and the Mach 30 modelling language (M30ML).
+M30ML was chosen since it had extensible ontology language, supports both textual and graphical view generation, lightweight textual syntax, and relatively minimal overhead with modern doctools.
+The other candidates lacked in many regards compared to M30ML in these criteria and thus, M30ML was selected.
+
+The SeaLion Architecture uses M30ML to specify references, stakeholder needs, user stories, and data structures for facilitating traceability of design decisions within the Mission Concept of Operations (ConOps) \cite{mach30_git}.
+The SeaLion repository is also structured as a Distributed Open Source Hardware (OSHW) Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
+
+This is all done in an effort to execute the project via a docs-as-code philosophy.
+A philosophy in which documentation is written with the same tools as code \cite{docs_as_code}.
+This allows for workflows between development teams to be more closely integrated.
 
@@
 
+M30ML was developed using the Ontological Modeling Language (OML) as its basis.
 OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite{oml_language}.
 OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.
-Thus, OML served as a useful basis to create the m30ml since both run on similar philosophies to simplify usage for the end user.
-
-\section{Mach30 Modelling Language}
-
-The SeaLion Architecture uses m30ml to specify references, stakeholder needs, user stories, & data structures for facilitating traceability of design decisions within the Mission ConOps \cite{mach30_git}.
-The SeaLion repository is also structured as a Distributed Open Source Hardware (OSHW) Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
-
-This is all done in an effort to execute the project via a documentation as code philosophy.
-A philosophy in which documentation is written with the same tools as code \cite{docs_as_code}.
-This allows for workflows between development teams to be more closely integrated.
 
@@
 
-The m30ml is a YAML-based modeling language for defining a software architecture.
+The M30ML is a YAML-based modeling language for defining a software architecture.
 Since YAML is a lightweight, highly-structured, human-readable, machine queryable, and line-oriented markup language, it was ideal for document generation use cases, as well as use with version control tools like Git.
@@
 
-Mach30 also had minimal technical overhead as it was compatible with modern doc tools such as asciidoctor & bibtex.
-
-Mach30 also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, and data structures, with relationship elements for defining traceability between modeling elements.
-
-For the aforementioned reasons, the SeaLion CubeSat flight software team downselected m30ml for specifying the SeaLion CubeSat flight software architecture \cite{mach30_git}.
+M30ML also had minimal technical overhead as it was compatible with modern doc tools such as asciidoctor & bibtex.
+M30ML also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, and data structures, with relationship elements for defining traceability between modeling elements \cite{mach30_git}.
 
@@
 
-The m30ml file structure for architecture is simple and easy to use.
+The M30ML file structure for architecture is simple and easy to use.
 Architecture is split into the four folders of references, stakeholder needs, user stories, and datastructures.
@@
 
-The following PLACEHOLDER TABLE, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the m30ml structure and injected directly into this article.
+The following PLACEHOLDER TABLE, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the M30ML structure and injected directly into this article.
 Should any changes be made to the SeaLion architecture repository, the tables can be immediately regenerated for continous updates.
@@
 
-The SeaLion project's methodology documentation uses m30ml based on YAML architecture modeling tools.
+The SeaLion project's methodology documentation uses M30ML based on YAML architecture modeling tools.
 The first step to build the architecture is to define the stakeholder needs.
@@
 
-\section{Future Work}
-
-PLACEHOLDER
-
 \section{Conclusion}
 
-PLACEHOLDER
+The approach and methodology presented in this article is done as an effort to reduce the painpoints associated with traditional systems engineering for the CubeSat developers.
+The ever growing number of CubeSat projects in existence demands a lightweight model-based approach that can be adopted for implementing flight software while minimizing configuration management overhead.
+Especially as many CubeSat developers will be new to the development environment.
+Docs-as-code combined with MBSE can be used as an approach to flight software for tight coupling between both software and documentation as well as providing a highly structured template to base future developments on for the CubeSat community cite{sealion_mission_architecture}.
+Future actions include validating this approach as the flight software is created based on the model-based docs-as-code approach with the upcoming SeaLion launch as well as further expanding the potential users of M30ML.
 
-\section*{Acknowledgments}
-An Acknowledgments section, if used, \textbf{immediately precedes} the References.
-Sponsorship information and funding data are included here.
-The preferred spelling of the word ``acknowledgment'' in American English is without the ``e'' after the ``g.'' Avoid expressions such as ``One of us (S.B.A.) would like to thank\ldots'' Instead, write ``F.~A.~Author thanks\ldots'' Sponsor and financial support acknowledgments are also to be listed in the ``acknowledgments'' section.
-
-\bibliography{manuscript_references}
+\bibliography{manuscript-references}
 

### 2022-12-08 buildDocs.sh
fix condition to check pdflatex version

@@ -199,7 +199,7 @@ cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls 
 # https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
 cmd="pdflatex manuscript.tex && bibtex manuscript.aux && pdflatex manuscript.tex && pdflatex manuscript.tex"
 dockercmd="docker run --rm -v $PWD/dist:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
-condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
+condition="pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
 
 if ! eval $condition; then
     echo "Generating PDF document from LaTeX document of manuscript via docker..."

### 2022-12-08 buildDocs.sh
set path vars for cd'ing into when clitool exists

@@ -111,35 +111,44 @@ fi
 #echo "generating abstract.pdf..."
 #docker run --rm --volume $PWD:/src -w "/src" asciidoctor/docker-asciidoctor asciidoctor research/abstract.adoc -o dist/abstract.pdf -r asciidoctor-pdf -r asciidoctor-diagram -r asciidoctor-bibtex -b pdf
 
+#### set environment variable for project root ####
+project_root=$PWD
+
 #### generate example manuscript ####
 # for linkml docker command usage, see https://hub.docker.com/r/linkml/linkml
 
 clitool="linkml-validate"
 cmdargs="-s manuscript-metamodel.yaml manuscript-example.yaml"
 cmd="$clitool $cmdargs"
-dockercmd="docker run --rm -v $PWD/manuscript:/work -w /work linkml/linkml:1.3.14 $cmd"
+workdir=$project_root/manuscript
+dockercmd="docker run --rm -v $workdir:/work -w /work linkml/linkml:1.3.14 $cmd"
 condition="$clitool --help | grep 'Validates instance data' > /dev/null"
 
 if ! eval $condition; then
     echo "Validating linkml model of example manuscript via docker..."
+    cd $project_root
     eval $(echo $dockercmd)
 else
     echo "Validating linkml model of example manuscript..."
+    cd $workdir
     eval $cmd
 fi
 
 clitool="jinja2"
 cmdargs="-o dist/manuscript-example.tex --format yaml templates/manuscript-example.tex.jinja2 manuscript/manuscript-example.yaml"
+workdir=$project_root
 #cmdargs="-o dist/title.tex --format yaml templates/title.tex.jinja2 manuscript/manuscript-example.yaml"
 cmd="$clitool $cmdargs"
-dockercmd="docker run --rm -v $PWD:/work -w /work roquie/docker-jinja2-cli $cmdargs"
+dockercmd="docker run --rm -v $workdir:/work -w /work roquie/docker-jinja2-cli $cmdargs"
 condition="$clitool --version | grep 'v0.8.2' > /dev/null"
 
 if ! eval $condition; then
     echo "Generating LaTeX document from example manuscript linkml model and jinja2 template via docker..."
+    cd $project_root
     eval $(echo $dockercmd)
 else
     echo "Generating LaTeX document from example manuscript linkml model and jinja2 template..."
+    cd $workdir
     eval $cmd
[…]

### 2022-12-08 buildDocs.sh
remove non-example typos

@@ -183,11 +183,11 @@ dockercmd="docker run --rm -v $workdir/manuscript:/work -w /work linkml/linkml:1
 condition="$clitool --help | grep 'Validates instance data' > /dev/null"
 
 if ! eval $condition; then
-    echo "Validating linkml model of example manuscript via docker..."
+    echo "Validating linkml model of manuscript via docker..."
     cd $project_root
     eval $(echo $dockercmd)
 else
-    echo "Validating linkml model of example manuscript..."
+    echo "Validating linkml model of manuscript..."
     cd $workdir
     eval $cmd
 fi
@@ -201,11 +201,11 @@ dockercmd="docker run --rm -v $workdir:/work -w /work roquie/docker-jinja2-cli $
 condition="$clitool --version | grep 'v0.8.2' > /dev/null"
 
 if ! eval $condition; then
-    echo "Generating LaTeX document from example manuscript linkml model and jinja2 template via docker..."
+    echo "Generating LaTeX document from manuscript linkml model and jinja2 template via docker..."
     cd $project_root
     eval $(echo $dockercmd)
 else
-    echo "Generating LaTeX document from example manuscript linkml model and jinja2 template..."
+    echo "Generating LaTeX document from manuscript linkml model and jinja2 template..."
     cd $workdir
     eval $cmd
 fi

### 2022-12-08 buildDocs.sh
check two conditionals for LaTeX/BibTeX build

@@ -160,9 +160,8 @@ cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls 
 cmd="pdflatex manuscript-example.tex && bibtex manuscript-example.aux && pdflatex manuscript-example.tex && pdflatex manuscript-example.tex"
 workdir=$project_root/dist
 dockercmd="docker run --rm -v $workdir:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
-condition="$clitool -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
 
-if ! eval $condition; then
+if [ ! $(pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null) ] && [ ! $(bibtex -version | grep '0.99d' > /dev/null) ]; then
     echo "Generating PDF document from LaTeX document of manuscript via docker..."
     cd $project_root
     eval $(echo $dockercmd)
@@ -218,9 +217,8 @@ cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls 
 cmd="pdflatex manuscript.tex && bibtex manuscript.aux && pdflatex manuscript.tex && pdflatex manuscript.tex"
 workdir=$project_root/dist
 dockercmd="docker run --rm -v $workdir:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
-condition="pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null"
 
-if ! eval $condition; then
+if [ ! $(pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null) ] && [ ! $(bibtex -version | grep '0.99d' > /dev/null) ]; then
     echo "Generating PDF document from LaTeX document of manuscript via docker..."
     cd $project_root
     eval $(echo $dockercmd)

### 2022-12-08 buildDocs.sh
cd into project_root before copying files to dist/

@@ -154,6 +154,7 @@ fi
 
 echo "Copy LaTeX files and assets (required for generating PDF document) to dist/..."
 
+cd $project_root
 cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls assets/*
 
 # https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
@@ -211,6 +212,7 @@ fi
 
 echo "Copy LaTeX files and assets (required for generating PDF document) to dist/..."
 
+cd $project_root
 cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls assets/*
 
 # https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography

### 2022-12-08 buildDocs.sh
comment out example manuscript build

@@ -114,63 +114,63 @@ fi
 #### set environment variable for project root ####
 project_root=$PWD
 
-#### generate example manuscript ####
-# for linkml docker command usage, see https://hub.docker.com/r/linkml/linkml
-
-clitool="linkml-validate"
-cmdargs="-s manuscript-metamodel.yaml manuscript-example.yaml"
-cmd="$clitool $cmdargs"
-workdir=$project_root/manuscript
-dockercmd="docker run --rm -v $workdir:/work -w /work linkml/linkml:1.3.14 $cmd"
-condition="$clitool --help | grep 'Validates instance data' > /dev/null"
-
-if ! eval $condition; then
-    echo "Validating linkml model of example manuscript via docker..."
-    cd $project_root
-    eval $(echo $dockercmd)
-else
-    echo "Validating linkml model of example manuscript..."
-    cd $workdir
-    eval $cmd
-fi
-
-clitool="jinja2"
-cmdargs="-o dist/manuscript-example.tex --format yaml templates/manuscript-example.tex.jinja2 manuscript/manuscript-example.yaml"
-workdir=$project_root
-#cmdargs="-o dist/title.tex --format yaml templates/title.tex.jinja2 manuscript/manuscript-example.yaml"
-cmd="$clitool $cmdargs"
-dockercmd="docker run --rm -v $workdir:/work -w /work roquie/docker-jinja2-cli $cmdargs"
-condition="$clitool --version | grep 'v0.8.2' > /dev/null"
-
-if ! eval $condition; then
-    echo "Generating LaTeX document from example manuscript linkml model and jinja2 template via docker..."
-    cd $project_root
-    eval $(echo $dockercmd)
-else
-    echo "Generating LaTeX document from example manuscript linkml model and jinja2 template..."
-    cd $workdir
-    eval $cmd
-fi
-
-echo "Copy LaTeX files and assets (required for generating PDF document) to dist/..."
-
-cd $project_root
-cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls assets/*
-
-# https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
-cmd="pdflatex manuscript-example.tex && bibtex manuscript-example.aux && pdflatex manuscript-example.tex && pdflatex manuscript-example.tex"
-workdir=$project_root/dist
[…]

### 2022-12-08 buildDocs.sh
Fix LaTeX/BibTeX pipeline for sealion manuscript

@@ -216,16 +216,31 @@ cd $project_root
 cp -t dist/ manuscript/*.tex manuscript/*.bib manuscript/*.bst manuscript/*.cls assets/*
 
 # https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
-cmd="pdflatex manuscript.tex && bibtex manuscript.aux && pdflatex manuscript.tex && pdflatex manuscript.tex"
+cmd="pdflatex manuscript.tex && bibtex manuscript.aux"
 workdir=$project_root/dist
 dockercmd="docker run --rm -v $workdir:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
 
 if [ ! $(pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null) ] && [ ! $(bibtex -version | grep '0.99d' > /dev/null) ]; then
-    echo "Generating PDF document from LaTeX document of manuscript via docker..."
+    echo "Pre-Processing LaTeX document with BibTeX of manuscript via docker..."
     cd $project_root
     eval $(echo $dockercmd)
 else
-    echo "Generating PDF document from LaTeX document of manuscript..."
+    echo "Pre-Processing LaTeX document with BibTeX of manuscript..."
+    cd $workdir
+    eval $cmd
+fi
+
+# https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
+cmd="pdflatex manuscript.tex && pdflatex manuscript.tex"
+workdir=$project_root/dist
+dockercmd="docker run --rm -v $workdir:/srv -w /srv nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
+
+if [ ! $(pdflatex -version | grep '3.14159265-2.6-1.40.19' > /dev/null) ] && [ ! $(bibtex -version | grep '0.99d' > /dev/null) ]; then
+    echo "Generating PDF document from LaTeX/BibTeX document of manuscript via docker..."
+    cd $project_root
+    eval $(echo $dockercmd)
+else
+    echo "Generating PDF document from LaTeX/BibTeX document of manuscript..."
     cd $workdir
     eval $cmd
 fi

### 2022-12-08 buildDocs.sh
append git tag info to manuscript name in pdf

@@ -244,3 +244,7 @@ else
     cd $workdir
     eval $cmd
 fi
+
+gitdescribe=$(git describe --always --tags HEAD)
+newmanuscriptname=manuscript-$gitdescribe.pdf
+mv $workdir/manuscript.pdf $workdir/$newmanuscriptname

### 2022-12-08 buildDocs.sh
uncomment lines for building m30ml model

@@ -1,22 +1,22 @@
 #!/usr/bin/env bash
 
-## Install node_modules, if not already installed
-#if [ ! -r ./node_modules ]; then
-#    echo "Installing node_modules..."
-#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'npm ci'
-#fi
-#
-## Install m30mlTools/node_modules, if not already installed
-#if [ ! -r ./m30mlTools/node_modules ]; then
-#    echo "Installing m30mlTools/node_modules..."
-#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd m30mlTools && npm ci'
-#fi
-#
-## Install dof-helpers/node_modules, if not already installed
-#if [ ! -r ./dof-helpers/node_modules ]; then
-#    echo "Installing dof-helpers/node_modules..."
-#    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd dof-helpers && npm ci'
-#fi
+# Install node_modules, if not already installed
+if [ ! -r ./node_modules ]; then
+    echo "Installing node_modules..."
+    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'npm ci'
+fi
+
+# Install m30mlTools/node_modules, if not already installed
+if [ ! -r ./m30mlTools/node_modules ]; then
+    echo "Installing m30mlTools/node_modules..."
+    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd m30mlTools && npm ci'
+fi
+
+# Install dof-helpers/node_modules, if not already installed
+if [ ! -r ./dof-helpers/node_modules ]; then
+    echo "Installing dof-helpers/node_modules..."
+    docker run --rm --volume "$PWD:/src" -w "/src" node bash -c 'cd dof-helpers && npm ci'
+fi
 
 # Create dist/ directory, if none exists
 if [ ! -r ./dist ]; then
@@ -24,92 +24,92 @@ if [ ! -r ./dist ]; then
     mkdir dist/
 fi
 
-## copy operating-mode-as-fsm.puml to dist/...
-#echo "copying operating-mode-as-fsm.puml to dist/..."
-#docker run --rm -v $PWD:/src -w /src node bash -c 'cp ./components/sealion-cubesat/components/sealion-obc/components/dilophos/fsw-architecture/operating-mode-as-fsm.puml dist/'
-#
-## generate dist/component.yaml & symlink to architecture/ directory
[…]

### 2022-12-22 manuscript-example.tex
deploy: 454f330c66d188ebf03c354449d169693ad4a7b4

--- 2022-11-22 research/manuscript-example/main.tex
@@
+\tolerance=1
+\emergencystretch=\maxdimen
+\hyphenpenalty=10000
+\hbadness=10000
+
 \documentclass[conf]{new-aiaa}
@@
 \author{First A.
-Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B.
-Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
+Author and Second B.
+Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B.
+Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.} }
 \affil{Business or Academic Affiliation 1, City, State, Zip Code}
-\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
+
+\author{Third C.
+Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.} and Third C.
+Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.} }
 \affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
-\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
-\affil{Business or Academic Affiliation 2, City, State, Zip Code}
+
+\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author.} }
+\affil{}
 
@@
 The footnote on the first page should list the Job Title and AIAA Member Grade for each author, if known Authors do not have to be AIAA members.
+
 \end{abstract}
@@
 $K$  & trailing-edge (TE) nondimensional angular deflection rate
+
 \end{longtable*}}
@@
 \section{Introduction}
+
 \lettrine{T}{his} document is a \LaTeX{} template for preparation of papers for AIAA Technical Conferences.
@@
 
-Prefixes such as ``non,'' ``sub,'' ``micro,'' ``multi,'' and ``"ultra'' are not independent words; they should be joined to the words they modify, usually without a hyphen.
+Prefixes such as ``non,'' ``sub,'' ``micro,'' ``multi,'' and ``ultra'' are not independent words; they should be joined to the words they modify, usually without a hyphen.
 There is no period after the ``et'' in the abbreviation ``et al.'' The abbreviation ``i.e.,'' means ``that is,'' and the abbreviation ``e.g.,'' means ``for example'' (these abbreviations are not italicized).
@@
 \section{Conclusion}
+
 A conclusion section is not required, though it is preferred.
@@
 
-\section*{Appendix}
+\section{Appendix}
 
@@
 
-\section*{Acknowledgments}
+\section{Acknowledgments}
+
 An Acknowledgments section, if used, \textbf{immediately precedes} the References.

### 2022-12-22 manuscript.tex
deploy: 454f330c66d188ebf03c354449d169693ad4a7b4

--- 2022-12-06 research/manuscript-example/manuscript.tex
@@
 
-\title{Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code approach}
+\title{Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code Approach}
 
-\author{Sean Marquez and Kevin Chiu}
-\affil{Old Dominion University, Norfolk, VA, 23529}
-\author{Sharan Asundi, Ph.D. \footnote{Assistant Professor, Department of Mechanical & Aerospace Engineering, Old Dominion University}}
-\affil{Old Dominion University, Norfolk, VA, 23529}
+\author{Sean Marquez and Kevin Chiu\footnote{Graduate Student, Mechanical and Aerospace Engineering.} }
+\affil{Old Dominion University, Norfolk, VA, 23529, USA}
+
+\author{Sharanabasaweshwara Asundi\footnote{Assistant Professor, Mechanical and Aerospace Engineering, and AIAA Professional Member.} }
+\affil{Old Dominion University, Norfolk, VA, 23529, USA}
 
@@
 \begin{abstract}
-PLACEHOLDER
+With the growing community of CubeSat developers has emerged a need for a technical approach that would provide a means of fast-tracking the lifecycle development process of CubeSats, including the need to minimize design and development time repeating prior engineering efforts.
+In addition to a technical approach, there is also the need for a language and toolchain with a demand for both minimal training and minimal IT overhead to configure.
+A model-based approach has become a topic of interest in addressing much of these systems engineering painpoints.
+However, the current state-of-the-art tools demand either considerable investment in training and/or IT overhead, making it difficult for CubeSat developers of small startups or academia to participate.
+This article presents a model-based technical approach in conjunction with a docs-as-code approach, used to fascilitate flight software architecture development, intended to guide an implementation, for the SeaLion CubeSat mission - a joint CubeSat mission between the Old Dominion University and Coast Guard Academy.
+The technical approach discussed in this paper was also used to model and generate the paper as itself.
+
 \end{abstract}
@@
 
+\begin{center}
 {\renewcommand\arraystretch{1.0}
@@
 \end{longtable*}}
+\end{center}
 
 \section{Introduction}
-\lettrine{T}{his} article presents the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, & implementation of the SeaLion mission architecture for the flight software using a model-based approach.
 
-A model-based systems engineering (MBSE) approach to systems engineering is where models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification & validation of a system \cite{architecting_spacecraft}.
-The NASA handbook on systems engineering can be applied to CubeSat Mission design, in effort to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture cite{asundi13_cubes}.
+\lettrine{T}{his} article presents the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, \& implementation of the SeaLion mission architecture for the flight software using a model-based approach.
 
-For the SeaLion Mission, the flight software team adopted an MBSE approach to flight software architecture using a document as code, also known as docs-as-code, approach \cite{docs_as_code}.
-This approach is where the same tools and methodologies for managing software are also used for configuration management of documentation.
-Applying both a MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured are within a model that is both human-readable and machine-queryable while minimizing configuration management overhead.
-A docs-as-code toolchain is also a file-based approach that allows for models to be persistent on local file systems without the additional use of cloud-based software or services.
+A model-based systems engineering (MBSE) approach to systems engineering is where models, as opposed to documents, serve as the authoritative source of truth for conducting systems engineering activities, such as the design, specification, analysis, verification \& validation of a system \cite{architecting_spacecraft}.
+The NASA handbook on systems engineering can be applied to CubeSat Mission design, in effort to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.
+
+For the SeaLion Mission, the flight software team adopted an MBSE approach to flight software architecture using a documentation as code, also known as docs-as-code, approach \cite{docs_as_code}.
+This approach adopts the principles and practices of good modern software development for configuration management of documentation.
+A docs-as-code approach also ensures source code and documentation can remain in sync, by virtue of treating the documentation as part of the software source code using the same version control system to manage both.
+Applying both a MBSE and docs-as-code approach means that aspects of the mission architecture, such as stakeholder needs, user stories, and data structures pertaining to the CubeSat mission, are captured within a human and machine-readable model, while minimizing configuration management overhead.
+A docs-as-code approach is also file-based, allowing data to persistent on the local filesystem, as opposed to a cloud database, eliminating the need for a constant internet connection, which is a considerable bottleneck for teams or teammates in conditions where an internet connection is otherwise inaccessible.
 
@@
 Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research, that were previous monopolized by much larger satellites, due to the low cost of production and launch of these satellites.
-As such, there has been increasing popularity for CubeSats as seen by the increasing number of launches in \ref{swartwout_data_graph} since inception \cite{swartwout_data}.
+As such, there has been increasing popularity for CubeSats as seen by the increasing number of launches in figure \ref{swartwout_data_graph} since inception \cite{swartwout_data}.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{swartwout_data_graph}
+    \includegraphics[width=.8\textwidth]{swartwout_data_graph}
     \caption{Nanosatellite launch data provided by M. Swartwout \cite{swartwout_data}.}
@@
 
-It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same tools used to manage code, using version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite{docs_as_code}.
+It was of interest to adopt a docs-as-code approach, as to yield the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of flight software architecture documentation, captured in a model-based approach \cite{docs_as_code}.
 It also allows for models to be persistent on a local file system without use of cloud-based services or software.
 
-\section{Mach30 Modelling Language}
+\section{Modeling Language, Tool, \& Methodology}
 
 The flight software team conducted a trade study to downselect a suitable modeling language for the afformentioned goals.
-The languages considered with SysML V1, SysML V2, PlantUML, and the Mach 30 modelling language (M30ML).
-M30ML was chosen since it had extensible ontology language, supports both textual and graphical view generation, lightweight textual syntax, and relatively minimal overhead with modern doctools.
+The languages considered were SysML V1, SysML V2, PlantUML, and the Mach 30 modelling language (M30ML).
+M30ML was chosen for its lightweight human and machine-readable textual syntax, file-based model-interchange support (for persisting models directly on the local filesystem), ability to generate both textual and graphical views, and relatively minimal overhead with modern doctools \cite{mach30_git}.
 The other candidates lacked in many regards compared to M30ML in these criteria and thus, M30ML was selected.
-
-The SeaLion Architecture uses M30ML to specify references, stakeholder needs, user stories, and data structures for facilitating traceability of design decisions within the Mission Concept of Operations (ConOps) \cite{mach30_git}.
-The SeaLion repository is also structured as a Distributed Open Source Hardware (OSHW) Framework (DOF)-component for defining the contents of the Mission ConOps as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs), assembly instructions, and/or usage documentation.
-
-This is all done in an effort to execute the project via a docs-as-code philosophy.
-A philosophy in which documentation is written with the same tools as code \cite{docs_as_code}.
-This allows for workflows between development teams to be more closely integrated.
 
@@
 M30ML was developed using the Ontological Modeling Language (OML) as its basis.
-OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite{oml_language}.
+OML is a language that \"enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}.\" OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite{oml_language}.
 OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.
 
-\subsection{Modeling Language, Tool, & Methodology}
+\subsection{Mach30 Modelling Language}
 
-The M30ML is a YAML-based modeling language for defining a software architecture.
+M30ML is a language for modeling an architecture YAML-based modeling.
 Since YAML is a lightweight, highly-structured, human-readable, machine queryable, and line-oriented markup language, it was ideal for document generation use cases, as well as use with version control tools like Git.
-The following \ref{user_story} showcases the simplicity of the YAML file.
+The following figure \ref{user_story} showcases the simplicity of the YAML file.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{ping_satellite}
+    \includegraphics[width=.8\textwidth]{ping_satellite}
     \caption{An example YAML file for a user story.}
@@
 
-M30ML also had minimal technical overhead as it was compatible with modern doc tools such as asciidoctor & bibtex.
+M30ML also had minimal technical overhead as it was compatible with modern doc tools such as asciidoctor \& bibtex.
 M30ML also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, and data structures, with relationship elements for defining traceability between modeling elements \cite{mach30_git}.
@@
 
-The following PLACEHOLDER TABLE, PLACEHOLDER TABLE, and PLACEHOLDER TABLE are all automatically generated using the M30ML structure and injected directly into this article.
-Should any changes be made to the SeaLion architecture repository, the tables can be immediately regenerated for continous updates.
+The following figure \ref{stakeholder-needs-mapping}, figure \ref{user-stories-mapping}, and figure \ref{data-structures-mapping} UML diagrams are auto-generated artifacts rendered from the M30ML modeling language and formatted using the Liquid template language.
+Should any changes be made to the SeaLion mission architecture model, these tables and diagrams can be immediately regenerated for continous updates, ensuring changes affecting dependencies within the mission architecture are kept in sync.
 
@@
 The two primary stakeholders for Sealion are ODU and CGA with their respective needs categorized on priority from primary to secondary to tertiary.
-These stakeholder needs are listed in the following Table PLACEHOLDER.
+These stakeholder needs are listed in the following figure \ref{stakeholder-needs-mapping}.
 
-PLACEHOLDER TABLE
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=.8\textwidth]{stakeholder-needs-mapping}
+    \caption{a view describing a mapping of stakeholders to stakeholder needs as a UML diagram}
+    \label{stakeholder-needs-mapping}
+\end{figure}
 
@@
 These are created from the perspective of the ground station operator to define the tasks that need to be completed to satisfy the user stories.
-These user stories are listed in the following Table PLACEHOLDER.
+These user stories are listed in the following figure \ref{user-stories-mapping}.
 
-PLACEHOLDER TABLE
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=.8\textwidth]{user-stories-mapping}
+    \caption{a view describing a mapping of stakeholder needs to their derived user stories as a UML diagram}
+    \label{user-stories-mapping}
+\end{figure}
 
+Alternative views can also be rendered from a model. For example, the user stories can also be rendered as a use case diagram \ref{use-case-diagram}.
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=.8\textwidth]{use-case-diagram}
+    \caption{a view describing user stories as a usecase diagram}
+    \label{use-case-diagram}
+\end{figure}
+\\
+\\
+\\
+\\
 \subsection{Example Data Structure}
 
-An example data structure can be derived from user stories as presented in Table PLACEHOLDER.
+A colletion of data structures can be derived from user stories as presented in figure \ref{data-structures-mapping}.
 
-PLACEHOLDER TABLE
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=.8\textwidth]{data-structures-mapping}
+    \caption{a view describing a mapping of user stories to their derived data structures as a UML diagram}
+    \label{data-structures-mapping}
+\end{figure}
+
+Because models are both human and machine readable, thus, a specification document can also be generated.
+For example, the following table \ref{satellite-health-data-packet} rendering of the data structure of the satellite health data packet:
+
+\begin{table}
+    \centering
+    \include{satellite-health-data-packet-as-table}
+    \caption{Satellite Health Data Packet}
+    \label{satellite-health-data-packet}
+\end{table}
+
+This manuscript document itself was also modeled and generated using the m30ml modeling language and toolchain.
 
@@
 Especially as many CubeSat developers will be new to the development environment.
-Docs-as-code combined with MBSE can be used as an approach to flight software for tight coupling between both software and documentation as well as providing a highly structured template to base future developments on for the CubeSat community cite{sealion_mission_architecture}.
+Docs-as-code combined with MBSE can be used as an approach to flight software for tight coupling between both software and documentation as well as providing a highly structured template to base future developments on for the CubeSat community \cite{sealion_mission_architecture}.
 Future actions include validating this approach as the flight software is created based on the model-based docs-as-code approach with the upcoming SeaLion launch as well as further expanding the potential users of M30ML.

### 2022-12-22 satellite-health-data-packet-as-table.tex
deploy: 454f330c66d188ebf03c354449d169693ad4a7b4

\begin{tabular}{ | m{3cm} | m{1cm}| m{1cm} | m{4cm} | } 
  \hline
  \textbf{Field} & \textbf{Type} & \textbf{Item Type} & \textbf{Description} \\
  \hline
  callsign & string &  & Identifying call sign for the Sealion mission. \\
  \hline
  batteryhealth & float &  & Percent value indicating the remaining charge of the batteries. \\
  \hline
  temperaturebattery & float &  & The temperature of the battery. Units in Kelvin. \\
  \hline
  mode & integer &  & Integer value indicating current mission mode. 0 = Safe, 1 = mission mode 1, 2 = mission mode 2, 3 = mission mode 3. \\
  \hline
  tledata & TLE &  & TLE data from orbit propogator at time of beacon. \\
  \hline

\end{tabular}

### 2023-04-17 manuscript/references.tex
Add mdpi journal content

\begin{thebibliography}{999}
    \bibitem{architecting_spacecraft}Friedenthal, S. \& Oster, C. Architecting spacecraft with SysML.  (2017)
    \bibitem{nasa_handbook}NASA NASA System Engineering Handbook. (NASA,2016)
    \bibitem{asundi13_cubes}Asundi, S. \& Fitz-Coy, N. CubeSat mission design based on a systems engineering approach. {\em 2013 IEEE Aerospace Conference}. pp. nil (2013,3), http://dx.doi.org/10.1109/AERO.2013.6496900
    \bibitem{scitech_proceeding}Sean Marquez, S. Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code approach. {\em AIAA Scitech Conference 2023}. (2023,1), https://arc.aiaa.org/doi/10.2514/6.2023-1126
    \bibitem{cds_rev14}The CubeSat Program, C. CubeSat Design Specification Rev. 14. (The CubeSat Program, Cal Poly SLO,2022)
    \bibitem{sealion_cdr}Academy, O. Critical Design Review: Mission SeaLion - ODU/CGA 3U CubeSat.  (2022)
    \bibitem{heidt_new}Heidt, H., Puig-Suari, J., Moore, A., Nakasuka, S. \& Twiggs, R. CubeSat - A new generation of picosatellite for education and industry low-cost space experimentation. {\em AIAA/USU Annual Conference On Small Satellites, 12th, Utah State University, Logan; UNITED STATES; 21-24 Aug.2000}. (2000,8), https://www.proquest.com/conference-papers-proceedings/cubesat-new-generation-picosatellite-education/docview/27219077/se-2
    \bibitem{sealion_cdr}Academy, O. Critical Design Review: Mission SeaLion - ODU/CGA 3U CubeSat.  (2022)
    \bibitem{heidt_new}Heidt, H., Puig-Suari, J., Moore, A., Nakasuka, S. \& Twiggs, R. CubeSat - A new generation of picosatellite for education and industry low-cost space experimentation. {\em AIAA/USU Annual Conference On Small Satellites, 12th, Utah State University, Logan; UNITED STATES; 21-24 Aug.2000}. (2000,8), https://www.proquest.com/conference-papers-proceedings/cubesat-new-generation-picosatellite-education/docview/27219077/se-2
    \bibitem{swartwout_data}Swartwout, M. CubeSat Database.  (2021), https://sites.google.com/a/slu.edu/swartwout/cubesat-database
    \bibitem{pumpkin_cubesat}Shop, C. Pumpkin CubeSat Kits.  (2023,3), https://www.cubesatshop.com/product/pumpkin-cubesat-kits/
    \bibitem{cubesat_handbook}Cappelletti Cubesat handbook: From mission design to operations. (Elsevier Science \& Technology,2020)
    \bibitem{reliving_24}Swartwout, M. Reliving 24 Years in the Next 12 Minutes: A Statistical and Personal History of University-Class Satellites.  (2018), https://digitalcommons.usu.edu/cgi/viewcontent.cgi?article=4277\&context=smallsat
    \bibitem{aalto}Praks AALTO-1 earth observation cubesat mission — Educational outcomes. {\em IEEE International Geoscience And Remote Sensing Symposium (IGARSS)}. (2015)
    \bibitem{howtosetup}Berthoud, M. How to Set Up a CubeSat Project - Preliminary Survey Results. {\em 30th Annual AIAA/USU Conference On Small Satellites}. (2016)
    \bibitem{sealion_mission_architecture}Team, S. SeaLion Mission Architecture. (Old Dominion University,2022), https://github.com/ODU-CGA-CubeSat/sealion-mission-architecture
    \bibitem{caesar_model_based_approach}David Wagner CAESAR Model-Based Approach to Harness Design. {\em Proceedings Of IEEE Aerospace Conference}. (2020,3)
    \bibitem{ibm_mbse}Brown, B. Model-based systems engineering: Revolution or evolution?.  (2011,12)
    \bibitem{docs_as_code}Holscher, E. Docs as Code.  (2022), https://www.writethedocs.org/guide/docs-as-code/
    \bibitem{mach30_git}Simmons, J. Mach30 Modeling Language. (Mach30 Foundation,2022), https://github.com/Mach30/m30ml
    \bibitem{sys_ml}Partners, S. SysML Specifications.  (2023), https://sysml.org/sysml-specs/
    \bibitem{sys_ml2}Submission Team, S. SysML-v2-Release.  (2023), https://github.com/Systems-Modeling/SysML-v2-Release
    \bibitem{plantuml}PlantUML PlantUML.  (2023), https://plantuml.com/
    \bibitem{oml_language}Maged Elaasar, N. Ontological Modeling Language: Origin and Rationale.  (2022), http://www.opencaesar.io/oml/
    \bibitem{oml_origin_and_rationale}Jenkinis, S. Ontological Modeling Language 1.4.  (2022), http://www.opencaesar.io/imce/2021/06/19/OML-Origin-and-Rationale.html
    \bibitem{sealion_dof}Team, S. Distributed OSHW Framework (DOF). (Old Dominion University,2023), https://odu-cga-cubesat.github.io/dof-cubesat/
    \bibitem{sealion_page}Team, S. SeaLion Mission Architecture. (Old Dominion University,2023), https://odu-cga-cubesat.github.io/sealion-mission-architecture/
\end{thebibliography}

### 2023-04-17 manuscript/template.tex
Add mdpi journal content

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosarticle, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypoarticle, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypoarticle, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Model Based Systems Engineering with a Docs-as-Code Approach for the SeaLion CubeSat Project}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Kevin Chiu $^{1,\dagger,\ddagger}$\orcidA{}, Sean Marquez $^{2,\ddagger}$ and Sharanabasaweshwara Asundi, PhD. $^{2,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Kevin Chiu, Sean Marquez and Sharanabasaweshwara Asundi}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Chiu K.; Marquez, S.; Asundi, A.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Old Dominion University; kchiu002@odu.edu\\
$^{2}$ \quad Old Dominion University; sasundi@odu.edu}

% Contact information of the corresponding author
\corres{Correspondence: kchiu002@odu.edu}

% Current address and/or shared authorship
\firstnote{Old Dominion University: Norfolk, VA, 23529, USA} 
\secondnote{These authors contributed equally to this work.}

% Contact information of the corresponding author
%\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The SeaLion flight architecture team for the SeaLion CubeSat project used a model based system engineering with docs-as-code approach to improve planning and organization of the project.  This was done in response to the growing number of University CubeSat teams with untrained students and personnel.  The team created tools for the systems architecture with the Mach 30 Modeling Language to create a architecture that is easy to learn and use even for newly admitted team members with little to no training. These tools can also generate documents via its own code for easy presentaton on a local file system without any proprietary software.}

% Keywords
\keyword{systems engineering; CubeSat; MBSE}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.

\section{Introduction}

Presented here is the systems engineering approach of the SeaLion CubeSat mission architecture.  This includes the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, and implementation of the SeaLion mission architecture for the flight software using a model-based approach.  Through, model-based systems engineering (MBSE), the SeaLion flight software team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.  These models were used to conduct activities such as design, specification, analysis, verification and validation of the system.  This was done by applying the NASA handbook on systems engineering \cite{nasa_handbook} to CubeSat mission design in efforts to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.

\subsection{CubeSat}
The CubeSat, originating from California Polytechnic State University in 1999, are a standardized form of nanosatellites.  Nanosatellites are satellites typically defined with a mass of less than 10 kg.  CubeSats, also known as Cube Satellites, are defined by the standardized and modular architecture of 1-Unit (1U) cube with dimensions of 10 cm X 10 cm X 10 cm with a mass of up to 2 kg \cite{cds_rev14}.  They can be scaled to 2-Units (2U), 3-Units (3U), or higher depending on units added as shown in figure \ref{fig:cubesat_family} with sizes designated by the CubeSat specification \cite{cds_rev14}.  This is done by the additional of standardized cube units to upscale the CubeSat.  The ability to scale by modularity gives a highly standardized structure for ease of expansion to provide versatility in functionality.  Due to their small size, mass, and lack of dedicated launch vehicles, CubeSats are typically launched as secondary payloads in conjunction with other larger satellites, informally known as “piggy-backing”.  This greatly decreases the cost of launching a CubeSat which greatly increases the accessibility of inserting objects into space.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/cubesat_family.png}
    \caption{CubeSat family by size \cite{cds_rev14}}
	\label{fig:cubesat_family}
    \end{figure}   
\unskip

\subsection{SeaLion Mission}
The SeaLion CubeSat mission is a joint project between Old Dominion University (ODU), the United States Coast Guard Academy (USCGA), and the Air Force Institute of Technology (AFIT).  The end goal is to produce a 3U CubeSat consisting of 3 payloads for on-orbit validation.  ODU provided one payload while the USCGA and AFIT provided the other two payloads.  SeaLion was initially planned to launch as a secondary payload on a Northrop Grumman Antares Rocket from Wallops Flight Facility (WFF) during March of 2023 \cite{sealion_cdr}.  The prototype CubeSat model is shown in figure \ref{fig:cubesat_blowup}.  The intended mission profile was to have an no-orbit time for mere days due to its planned very low earth orbit (VLEO) altitude.  Thus, SeaLion was to complete validation of its payloads before either power is lost in its non-rechargeable batteries or the satellite reenters and burns up in Earth's atmosphere.  The predicted on-orbit time was 10 days.  However, weight considerations on the planned Antares caused SeaLion to be moved to a Q4 launch on a Firefly rocket from Vandenberg Space Force Base into a sun synchronous orbit, of 500 miles altitude.  The content presented in this article is based on the prior mission profile from the launch at WFF into VLEO.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/cubesat_blownup.png}
    \caption{Blownup SeaLion CubeSat Prototype}
	\label{fig:cubesat_blowup}
    \end{figure}
	\noindent   
\unskip

The payloads are as follows. The first payload is provided by the USCGA and AFIT, is the Impedance Probe (IP).  The IP is derived from U.S. Naval Research Laboratory's (NRL's) 'Space PlasmADiagnostic suitE' (SPADE) aboard NASA's International Space Station (ISS) where plasma density and temp are computed with alternating current (AC) impedance measurements using an innovative, first of its kind surface mounted dipole radio frequency antenna \cite{sealion_cdr}.  The IP part is shown in figure \ref{fig:IP}.

\begin{figure}[H]
    \includegraphics{Definitions/impedence.png}
    \caption{Impedence Probe}
	\label{fig:IP}
    \end{figure}
	\noindent   
\unskip

The second payload, provided by the USCGA and AFIT, is the multispectral (Me-S) 'Pixel Sensor' with a with a 450 nm - 1000 nm spectral range \cite{sealion_cdr}.  Its purpose is to provide SeaLion's in-situ spectral data as a baseline.  This baseline will be used for future missions that may require this spectral data.  The Me-S part is shown in figure \ref{fig:Me-S}.

\begin{figure}[H]
    \includegraphics{Definitions/spectral.png}
    \caption{Me-S 'Pixel Sensor'}
	\label{fig:Me-S}
    \end{figure}
	\noindent   
\unskip

The third payload, provided by ODU, is the deployable composite structure (DeCS).  This payload is a proof-of-concept deployable mechanism and composite boom that is meant to be a platform host to a number of number of applications \cite{sealion_cdr}.  For example, these applications include solar panels, solar sails, drag sails, sensory sails, and magnetometer booms.  Deployment on SeaLion is meant to validate the deployable mechanism for composite boom in the space environment and to validate boom dynamic during and after deployment in orbit.  The DeCS upon deployment is shown in figure \ref{fig:DeCS}.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/decs.png}
    \caption{DeCS as the black popout booms}
	\label{fig:DeCS}
    \end{figure}
	\noindent   
\unskip

The SeaLion flight software team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team.  Three separate payloads require care and attention to ensure success.  The results of this effort are presented in this article.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
\subsection{CubeSat Populations}

CubeSats were initially conceived as educational tools for space systems engineering \cite{heidt_new}.  Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these CubeSat satellites.  As such, there has been increasing popularity for CubeSats as seen by the number of launches in figure \ref{fig:launch_data} since year 2000 \cite{swartwout_data} apart from the notable exceptions in the years 2020 and 2021; the author speculates that this downturn is due to the COVID-19 pandemic.  The CubeSat design specification \cite{cds_rev14} as well as the availability of commercial off-the-shelf (COTS) parts and kits have greatly influenced the rise of popularity.  For example, a basic CubeSat kit from Pumpkin can be purchased with a baseline price of as little as 6250 US dollars \cite{pumpkin_cubesat}.  Even the SeaLion CubeSat utilizes many COTS parts as well.  Thus, it has become highly accessible to low-budget groups such as small companies and university groups.  CubeSats have caused the “democratization” of space due to their low cost which has allowed many groups to fly satellites \cite{cubesat_handbook}.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/launch_data.png}
    \caption{Nanosatellite launch data provided by M. Swartwout as of July 21, 2021 \cite{swartwout_data}}
	\label{fig:launch_data}
    \end{figure}
	\noindent   
\unskip

University groups especially are a large contributor in the overall number of launches of CubeSats yearly.  As of July 27, 2021, alone, there have been 68 CubeSat launches with 40 of them being from university groups (about 58 percent of launches) in the year of 2021; university groups have consistently maintained plurality on total launches \cite{swartwout_data}.  This showcases directly how many university-based CubeSat projects occurred or potentially may occur if trends continue onwards into the future.  However, this poses challenges to many of these projects given the mainly student composed teams which includes the SeaLion mission at ODU.

\subsection{Ensuring CubeSat Success}
The increased number of CubeSats launched also means a greater number of CubeSats from universities being launched as well.  The motivation of this article is to improve the success rate of CubeSat missions from university groups by providing readily available and easily usable tools for university teams.  To further reinforce the need to improve the success rate, the following data is presented in figure \ref{fig:mission_status} which showcases the total successes and failures of CubeSats from universities for the given time periods \cite{reliving_24}.  The data provided is categorized by six different mission statuses of unknown, launch fail, dead on arrival (DOA), early loss, partial mission, and full mission.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/mission_status.png}
    \caption{Mission status of CubeSat university-class missions provided by Swartwout}
	\label{fig:mission_status}
    \end{figure}
	\noindent   
\unskip

As seen in the preceding figure \ref{fig:mission_status}, failure rates over time appear to be increasing among CubeSats launched from universities.  However, Swartwout notes that highest number of the failures originate from “regular independent” groups with a failure rate of 65 percent at the time of data gathering in 2017 \cite{reliving_24}.  These “regular independent” groups are groups that have fewer than four missions nor designated as a national center of for spacecraft development by its government.

The issue present is that many of the growing number of university groups producing CubeSats lack the resources, training, experience, or methodology to reliably give assurance to their missions.  Often, the majority of the work is done by untrained university students that are, many times, unfamiliar with the system engineering, design methodologies, testing, etc. that are associated with CubeSat development.  The SeaLion team also faced these issues as well.

To address some of these issues, the SeaLion flight software team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.  These provided system engineering approaches and tools include factors such as planning, documentation, project management, and simplifying the process.  Special attention should be given to systems engineering and information exchange for multidisciplinary teams \cite{aalto}.  To showcase these factor's importance, a survey conducted, by University of Bristol, on how to set up CubeSat projects of forty CubeSat groups emphasized the following relevant lessons learned \cite{howtosetup}:

\begin{itemize}
	\item	Planning: Make efforts to “spend a lot of time in the planning stage”.;
	\item	Documentation / Project Management: Groups should have “good documentation of requirements, work done and work to do”.;
	\item	Simplicity: Simply anything you possibly can to increase confidence in success.
\end{itemize}

The developed mission architecture and associated tools will emphasize the aforementioned points to further the SeaLion CubeSat's development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Goals}

The goal of the SeaLion CubeSat mission architecture was to capture the data structures and expected behaviors for the development of the flight software.  It has to be done such that it can unambiguously understood well enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.  Thus, the SeaLion CubeSat mission architecture had to achieve the following:

\begin{itemize}
	\item	Ensure templates only contain formatting data (this includes not storing boilerplate text in templates);
	\item	Ensure models are the authoritative source of truth for all artifact content (e.g., artifact structure, meta-data, boilerplate, commentary, discussion, diagrams, tables, etc.);
	\item 	Models should persist on the local filesystem.;
	\item 	Documents should be in plaintext as to be compatible with modern distributed version control system (e.g., Git) and for ease of use.;
	\item 	Documents should be able to sit alongside code and speak to one another.;
	\item 	Documents should be model-based as to have a separation of concerns between content and formatting as well as be both human and machine-readable for querying and generating views.;
\end{itemize}

A MBSE approach was adopted by the Sealion CubeSat flight software team since it provided benefits such as reducing the ambiguity that usually comes with using informal language to specify systems or its various aspects.  It also minimized the duplication of content that tends to accumulate in a document-based system engineering approach.

Proper adoption of a MBSE approach also includes the selection of modeling language and modeling tool.  Considerations when selecting the modeling language and tool was overhead incurred from training the team, the technical overhead of setting up modelling tools, and future adaptability.  Refer to table \ref{tab:language} for modelling language down selection overview.  In addition, the Sealion CubeSat flight software team eventually decided to adopt a docs-as-code approach to further enhance the MBSE approach to achieve the listed goals shown above.

\subsection{Model-Based Systems Engineering}
As noted prior that attention should be given to as planning, documentation, project management, and simplifying the process.  That special emphasize should be given to systems engineering and information exchange \cite{aalto}.

Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.  Information in a traditional systems engineering approach today is mostly captured informally, not authored based on a methodology, configuration managed in silo tools, adhocly and infrequently integrated, not easily traceable to its provenance, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.  These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.

In contrast, a MBSE approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.  Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:

\begin{itemize}
	\item	Information is readily communicated and shared within the project.;
	\item	Changes are easily accommodated.;
	\item	Traceability is automated.
\end{itemize}

\subsection{Docs-As-Code Approach}
Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.  This allows for documentation to updated seamlessly without additional work with document tools (doctools).  The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio), etc.  To do so would mean that the “following the same workflows as development teams, and being integrated in the product team. It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{ibm_mbse}.  The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{ibm_mbse}.  In addition, these models can stored and used persistently on a local file system without the use of cloud based services.  Proprietary services are not required to generate documentation, modify documentation, or modify models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modelling Language and Methodology}
The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the flight software team conducting a trade study to determine the most suitable.  The down selection criteria that the SeaLion CubeSat flight software team has taken into consideration is shown in table \ref{tab:language}.

\begin{table}[H] 
	\caption{Modeling Language Downselect}
	\label{tab:language}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CCCCC}
	\toprule
	\textbf{Criteria}  & \textbf{SysML v1}  & \textbf{SysML v2}  & \textbf{PlantUML}  & \textbf{M30ML}\\
	\midrule
	Extensible ontology language                       & X        & X        & X        & X     \\ \hline
	Supports both textual \& graphical view generation &          & X        &          & X     \\ \hline
	Lightweight textual syntax                         &          & X        & X        & X     \\ \hline
	Relatively minimal overhead with modern doctools   &          &          & X        & X     \\ \hline
	Supports execution semantics                       &          & X        &          &       \\
	\bottomrule
	\end{tabularx}
\end{table}

M30ML was chosen for its lightweight human and machine-readable textual syntax, file-based model interchange support (for persisting models directly on the local filesystem), ability to generate both textual and graphical views, and relatively minimal overhead with modern doctools \cite{mach30_git}.  The lightweight textual syntax and minimal over head is especially important for for a team that had very minimal experience working with such tools.  Other candidate modelling languages lacked in many regards compared to M30ML in these criteria and thus, M30ML was selected.  SysML v2 had a good number of characteristics that M30ML had, however, the lack of minimal overhead with modern doctools prevented its adoption.

\subsection{Ontological Modeling Language}
M30ML was developed using the Ontological Modeling Language (OML) as its basis.  OML is a language that enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}.  OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of aforementioned standard for use in systems engineering \cite{oml_language}.  OWL2 does not conform easily to individual modelling rules without tooling support; thus, OML was created.  OML is a tool to improve the speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.

\subsection{Mach 30 Modeling Language}

M30ML is a language for modeling an architecture with YAML-based modeling.  YAML is especially important as a file structure since it is a highly structured, machine queryable, human-readable, lightweight, and line-oriented markup language.  This makes it ideal for document generation use cases as well as use with version control tools like Git.  The simple line by line structure as shown in figure \ref{fig:example_yaml} exemplifies its simplicity.  Users are easily able to read, interpret, and edit documents using the YAML file format so as long they are taught what each line element is.  Doctools such as asciidoctor and bibtex were made compatible easily with minimal technical overhead which was taken advantage of for the submission to the AIAA SciTech 2023 Forum \cite{scitech_proceeding}.  M30ML also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, data structures, and with relationship elements for defining traceability between modeling elements \cite{mach30_git}.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/user_story.png}
    \caption{Example YAML file}
	\label{fig:example_yaml}
    \end{figure}   
\unskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Architecture Implementation}
The implementation of M30ML serves as the basis for SeaLion mission architecture.  Presented here are the various elements, components, and products generated that is stored on the sealion-mission-architecture GitHub page \cite{sealion_mission_architecture}.  At the time of publication of this article, the implementation of the SeaLion mission architecture was done to the prior mission parameters where the SeaLion CubeSat was designed for a short lifespan compared to now greatly extended planned lifespan.  Since the mission parameters was changed rather recently prior to publication, the architecture had yet to be updated for them.

\subsection{File Structure}
The SeaLion mission architecture is organized into two main folders of architecture and of components \cite{sealion_mission_architecture}.  Architecture contains the references, stakeholder needs, user stories, and data structures shown in figure \ref{fig:folders}.  Components, as the name implies, contains the components and subcomponents of the CubeSat.  For the focus of this article, the architecture folder is the primary concern.  Components is currently a work in progress at time of publication of this article and will be addressed with other future required work.  For the mission architecture shown in figure \ref{fig:folders}, generally data structures are derived from user stories.  Further, user stories are subsequently derived from stakeholder needs with their respective references.

\begin{figure}[H]
    \includegraphics{Definitions/folders.png}
    \caption{Folder structure}
	\label{fig:folders}
    \end{figure}
	\noindent   
\unskip

References are simply stored reference material such as standards, specifications books, etc.  They are very simple two-line YAML files as shown in figure \ref{fig:reference_yaml}.  This creates a continued link between the YAML files within their respective folders from which documents can be updated seamlessly.  Information changed within one file can interact with other files.  All YAML references files in the mission architecture at the time of article's publication is listed within and figure \ref{fig:reference_file}.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/reference.png}
    \caption{References YAML file}
	\label{fig:reference_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/reference_file.png}
    \caption{References file structure}
	\label{fig:reference_file}
    \end{figure}   
\unskip

\subsection{Stakeholder Needs}
The development of SeaLion's mission architecture is guided by a series of stakeholder needs \cite{sealion_dof}.  After SeaLion's project methodology documentation is committed to using M30ML based on YAML modelling tools, the first step is to identify all stakeholder needs.  The two primary stakeholders of SeaLion are ODU and the CGA.  Their respective needs are classified from primary, secondary, and tertiary based on mission importance.

Stakeholder YAML files are stored in '1-StakeholderNeeds' shown in figure \ref{fig:folders}.  Each file is numbered with a X.X number format with the first number designating if it's primary, secondary, or tertiary and the second number denoting a place within a list of that class (e.g., 1.1 would indicate primary stakeholder need 1).  In addition, the letter associated (e.g., A1, B1, C1, etc.) in the filename would also signify if it's a primary, secondary, or tertiary stakeholder need. Each YAML file contains an id number, name, statement, and derivedFrom field shown in figure \ref{fig:stakeholder_yaml}.  Note the reference YAML file that has filed in the derivedFrom field that serves as the basis for the stakeholder need.  While not all stakeholder needs have it filled, it is available to be used as needed.  figure \ref{fig:stakeholder_file} showcases all the YAML files stored in the stakeholders file folder.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/stakeholder.png}
    \caption{Stakeholder YAML file}
	\label{fig:stakeholder_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/stakeholder_file.png}
    \caption{Stakeholders file structure}
	\label{fig:stakeholder_file}
    \end{figure}
	\noindent   
\unskip

Figure \ref{fig:uml_stakeholder} presents all the stakeholder needs via a unified modelling language (UML) diagram generated from the YAML files within the '1-StakeholderNeeds' folder.  The two primary stakeholders being ODU and the USCGA.  The generation of these diagrams via the YAML files presented herein showcases the docs-as-code approach.  YAML files structured as a code are then converted into easily human readable documents for presentation.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_stakeholder.png}
    \caption{Stakeholder UML Diagram}
	\label{fig:uml_stakeholder}
    \end{figure}   
\unskip

\subsection{User Stories}
Once the SeaLion mission architecture's stakeholder needs are identified and recorded, the stakeholder needs are then used to identify a series of user stories which then lead to design decisions captured in data structure and activity definitions \cite{sealion_page}.  These user stories are written from the perspective of the ground operator which would be a student from ODU who monitors and controls the functions of the SeaLion CubeSat.  User story YAML files are stored in '2-UserStories' folder shown in figure \ref{fig:folders}.  These files are all given an ID number in no particular order of importance.  See the following figure \ref{fig:userstory_file} for the user story YAML file structure.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/userstory_file.png}
    \caption{User stories file structure}
	\label{fig:userstory_file}
    \end{figure}
	\noindent   
\unskip

As an example, the second user story desire is to “verify that satellite is operating nominally” \cite{sealion_mission_architecture}.  Its full statement, derived from the actor, behavior, and rationale, would read “as a Ground Station Operator I want to view satellite beacon data (alternating between health and mission data), received via UHF so that I can verify that satellite is operating nominally” \cite{sealion_page}.  Its associated YAML file named '2-ViewBeaconData.yaml' is presented in figure \ref{fig:view_beacon}.  Note that this user story is derived from stakeholder needs A1, A3, A5, B1, B2, C1, C2, and C3 which are stakeholder needs mentioned in the prior section detailing stakeholder needs.  Additionally, the example statement is cut-off in figure \ref{fig:view_beacon} for readability.  It should read in full as “View satellite beacon data (health or mission data) to verify that state vector correspond with expected orbit profile and/or to validate that a mission mode was successful”.  This satellite beacon data, transmitted via UHF, is used to validate that any and all functions of the satellite are operating nominally or as planned in respect to their payloads hence the large derivedFrom list in the associated YAML file.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/view_beacon.png}
    \caption{View Beacon YAML structure}
	\label{fig:view_beacon}
    \end{figure}
	\noindent   
\unskip

Figure \ref{fig:uml_userstory} and figure \ref{fig:uml_userstory2} are UML diagrams generated using the YAML files stored in '2-UserStories' folder.  Figure \ref{fig:uml_userstory} is a mapping of stakeholder needs to user stories.  Figure \ref{fig:uml_userstory2} is the user stories presented in a use case diagram to showcase what the ground station operator needs to perform.  The generation of these diagrams via the YAML files presented herein showcases the docs-as-code approach.  YAML files structured as a code are then converted into easily human readable documents for presentation.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_userstory.png}
    \caption{UML diagram of user stories}
	\label{fig:uml_userstory}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_userstory2.png}
    \caption{UML diagram of ground station operator}
	\label{fig:uml_userstory2}
    \end{figure}   
\unskip

\subsection{Data Structures}
User stories once identified will then lead to design decisions captured in data structures and activity definitions.  These data structures are the data that would transmitted back and forth between ground station operator and CubeSat.  Data structure YAML files are stored in '3-DataStructures' folder shown in figure \ref{fig:folders}.  Each data structure YAML has name, purpose, template, elements, and derived from elements as shown in figure \ref{fig:datastructure} as an example.  Name and purpose are for identification and stated use case.  Template lists out all the elements that are called out via their identifying key.  Elements detail the specific values as part of the data structure; each element has their own identifying information and descriptions.  The derived from field is used to tie back the data structure to a user story YAML file should it be applicable.  Table \ref{tab:datastructure} is a table generated from the YAML file shown in figure \ref{fig:datastructure} for documentation purposes.  figure \ref{fig:datastructure_file} details the file structure under the 3-DataStructures' folder.

\begin{table}[H] 
	\caption{Data Structure of Packet}
	\label{tab:datastructure}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CCCC}
	\toprule
	\textbf{Field}  & \textbf{Type}  & \textbf{Item Type}  & \textbf{Description}\\
	\midrule
	call\_sign           & string         &  & Identifying call sign for the Sealion mission.                                                                         \\ \hline
	battery\_health      & float          &  & Percent value indicating the remaining charge of the batteries.                                                        \\ \hline
	temperature\_battery & float          &  & The temperature of the battery. Units in Kelvin.                                                                       \\ \hline
	mode                 & integer        &  & Integer value indicating current mission mode. 0 = Safe, 1 = mission mode 1, 2 =   mission mode 2, 3 = mission mode 3. \\ \hline
	state\_vector        & ECIStateVector &  & ECI state vector from orbit propogator at time of beacon. \\    
	\bottomrule
	\end{tabularx}
\end{table}

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/datastructure.png}
    \caption{Satellite Health Data Structure}
	\label{fig:datastructure}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/datastructure_file.png}
    \caption{Data structure File Structure}
	\label{fig:datastructure_file}
    \end{figure}
	\noindent   
\unskip

As shown in figure \ref{fig:datastructure}, the data structure, with YAML file named '1-SatelliteHealth.yaml' is for determining the satellite's health.  This data would be transmitted with the beacon data to be received by the ground station operator.  Note that this data structure is derived from the user stories 2 and 4.1 described in the prior section detailing user stories.  These user stories detail the ground station operator's tasks to view the satellite beacon data and to request satellite health data packet so that operator can verify that AODS sensors and GPS data are within nominal parameters.  Table \ref{tab:datastructure} details the various fields that would be required in this beacon data packet to accomplish the aforementioned tasks.

Figure \ref{fig:uml_datastructure} is a UML diagram of mapping of user stories to data structures generated from the YAML file shown in figure \ref{fig:datastructure}.  The generation of this diagram and the tables via the YAML files presented herein showcases the docs-as-code approach.  YAML files structured as a code are then converted into easily human readable documents for presentation.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_datastructure.png}
    \caption{UML Diagram of Data Structures}
	\label{fig:uml_datastructure}
    \end{figure}   
\unskip

\subsection{Document Generation}
As noted multiple times throughout this article, there have been a number of figures and tables generated from the YAML files placed within the SeaLion mission architecture GitHub repository.  Many of the figures are UML diagrams that are auto-generated artifacts rendered from the M30ML modeling language and formatted using the Liquid template language.  This is the link for the docs-as-code approach.  YAML code files are used to generate documents for information sharing between group members.  This means that any changes made to the SeaLion mission architecture model can immediately be used to generate new documents.  Whether it be diagrams, tables, or text, continuous updating is ensured that any changes affecting dependencies within the mission architecture are kept in sync.  A conference proceeding manuscript presented in AIAA SciTech 2023 was created purely by a docs-as-code format \cite{scitech_proceeding}.  The team used a LaTeX template to automatically format the manuscript to the conference guidelines and subsequently inject items such as the generated diagrams, tables, and references directly into the manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Component Implementation}
The implementation of M30ML for components is still a work in progress at the time of this article's publication.  A brief description of current component implementation into the SeaLion model is provided.  However, many of the implementation methods mentioned herein are subjected to change and are not finalized unlike the architecture described in the prior section.

\subsection{Distributed OSHW Framework}
The M30ML pillars are based on Open Source Hardware (OSHW) principals \cite{mach30_git}.  The current SeaLion mission architecture repository, at time of article publication, for components is “structured as a Distributed OSHW Framework (DOF) - component for defining the contents of the Mission concept of operations (ConOps) as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs) and assembly instructions for the SeaLion CubeSat” \cite{sealion_mission_architecture}.  Inside the components folder of the SeaLion mission architecture repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.  Each of those folders would contain a components folder and subsequently those individual labeled components can have their own components folder.  Thus, a chain of components and subcomponents can be created as illustrated in figure \ref{fig:components_file}.  A parts YAML file in each components folder details what the subcomponents would be.  An excerpt example for the main SeaLion cubesat is provided in figure \ref{fig:components} that is associated with the file folders shown in figure \ref{fig:components_file}.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/components_file.png}
    \caption{Components Folder File Structure}
	\label{fig:components_file}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/components.png}
    \caption{Component YAML File}
	\label{fig:components}
    \end{figure}   
\unskip

\subsection{Component Data Structure and File Implementation}
A series of YAML files for components have been created.  figure \ref{fig:components} showcases the parts YAML file, however, parts is only one element of the component's data structure thus far.  Showcased in table \ref{tab:component_data} is the entire component data structure from the SeaLion DOF templates \cite{sealion_dof}.  There are a number of component data structures prepared, however, it is still in contention whether or not all of these data structures will be used.  The SeaLion DOF templates document have been generated in the DOF repository \cite{sealion_dof}.  The data structures created are as follows:

\begin{itemize}
	\item	Component: Represents the smallest logical element in an OSHW project. A Component may be a project in its own right (with a sub-component hierarchy) or may be nested as a sub-component in the "source" of another component.;
	\item	Component List Item: Identifies a part or tool used in the fabrication of the component. Parts and tools are defined by their source material in the components list.;
	\item	Activity Step: Defines a single step in an activity, e.g., assembly instructions.;
	\item	Parameter: Defines a data structure for an input or output of a component function.;
	\item	Function: Defines a data structure for a component function.;
	\item	Interface List Item: Identifies an interface on a part or tool.;
\end{itemize}

\begin{table}[H] 
	\caption{Component Data Structure}
	\label{tab:component_data}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{adjustwidth}{-\extralength}{0cm}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\fulllength}{CCCC}
	\toprule
	\textbf{Field}  & \textbf{Type}  & \textbf{Item Type}  & \textbf{Description}\\
	\midrule
	name          & string     &                       & Source   representation of the component's name. Format = single word, only lowercase   letters, and may contain hyphens and underscores.                                   \\ \hline
	version       & string     &                       & Version   number of the component's source. Format = x.x.x per semantic versioning   guidelines.                                                                            \\ \hline
	description   & string     &                       & Human   readable representation of the component's name. Typically used in rendered   documentation referencing the component.                                              \\ \hline
	license       & string     &                       & List of   licenses used within the component's source. Format = SPDX license   expression.                                                                                  \\ \hline
	author        & string     &                       & Identifies   author (e.g. owner of source intellectual property). Format (email and   website are optional)= Author Name \textless{}email address\textgreater (website URL) \\ \hline
	dependencies  & dictionary & string                & Per   NPM/Yarn. Key = dependency name. Value = Semantic versioning version string.                                                                                          \\ \hline
	components    & dictionary & Component             & Listing   of sub-components directly owned by this component. Key = sub-component's   name. Value = sub-component's data structure.                                         \\ \hline
	parts         & dictionary & Component   List Item & Listing   of the component's parts (and substitutions) defined as sub-components. Key =   part's id. Value = part's key data.                                               \\ \hline
	functions     & list       & Function              & Listing   of component functions.                                                                                                                                           \\ \hline
	tools         & dictionary & Component   List Item & Listing   of the required tools (and substitutions) defined as sub-components. Key =   tool's id. Value = tool's key data.                                                  \\ \hline
	precautions   & list       & string                & Listing   of caution statements (e.g. safety warnings) for the component.                                                                                                   \\ \hline
	assemblySteps & list       & Activity   Step       & Sequence   of steps required to assemble the component. \\
	\bottomrule
	\end{tabularx}
	\end{adjustwidth}
\end{table}

The initial goal is to list the components of the SeaLion CubeSat and to generate assembly steps for them.  Through which the architecture can provide detailed documentation to assemble the SeaLion CubeSat.  These assembly instructions would also be generated through the SeaLion mission architecture repository much akin to other documents for SeaLion.  Thus, it creates an easily human readable document from the YAML files code as per the docs-as-code approach.

Eventually, the purpose of all these component data structures is to also create an N2 diagram.  An N2 diagram is used to “is used to capture the interfaces, mechanical and electrical, for all components of the satellite obtained through the mapping process” \cite{asundi13_cubes}.  An example has been provided in figure \ref{fig:N2}.  The end goal is that the architecture would use interfaces and junctions within the YAML files code to automatically generate an N2 diagram.  Thus, it allows for continuous updating that ensures that any changes affecting dependencies within the mission architecture are kept in sync.  This would allow for a team to easily identify “areas where conflicts could arise in interfaces, and highlights input and output dependency assumptions and requirements” \cite{asundi13_cubes}.  Thus, leading to higher efficacy in planning the development and assembly of the satellite.

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/N2.png}
    \caption{N2 Chart Example}
	\label{fig:N2}
    \end{figure}   
\unskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
The SeaLion flight software team used MBSE with docs-as-code approach to the SeaLion project. This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for the CubeSat developers.  This is particularly important when CubeSat projects are growing more numerous and with many of their respective team members being new to space systems development.   It has accomplished the ability to create individual elements of the architecture in an easily human readable code that is also easy to make revisions to.  Even for those who are unfamiliar with coding software or methods.  Thus, minimal training is required for usage.  It can also generate documents for easy presentation as well.Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{This research received no external funding.}

%\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data. In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Where no new data were created, or where data is unavailable due to privacy or ethical re-strictions, a statement is still required. Suggested Data Availability Statements are available in section “MDPI Research Data Policies” at \url{https://www.mdpi.com/ethics}.}

\acknowledgments{Special thanks to Dr. Sharan Asundi, PhD., Sean Marquez, and the SeaLion Project Team}

\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
1U &	1-Unit\\
2U &	2-Unit\\
3U &	3-Unit\\
AC &	Alternating Current\\
AFIT &	 Air Force Institute of Technology \\
AIAA &	American Institute of Aeronautics and Astronautics \\
AODS &	Altitude and Orbit Determination System\\
BOM &	Bill of Material\\
ConOps &	Concept of Operations\\
COTS &	Commerical Off-the-Shelf\\
DeCS &	Deployable Composite Structure\\
DOA &	Dead on Arrival\\
doctools &	Dcoument Tools\\
DOF &	Distributed OSHW Framework \\
EVR &	Event\\
GPS &	Global Positioning System\\
ISS &	International Space Station\\
M30ML &	Mach 30 Modelling Language\\
MBSE &	Model Based Systems Engineering\\
MC3 &	Mobile CubeSat Command and Control \\
Me-S &	Multi-spectral Sensor \\
NRL &	Naval Research Laboratory\\
ODU &	Old Dominion University\\
OML &	Ontological Modeling Language \\
OSHW &	Open Source Hardware\\
OWL2 &	Web Ontology Language 2 \\
Q4 &	Quarter Four\\
SPADE &	Space PlasmADiagnostic suitE\\
SWRL &	Semantic Web Rule Language \\
UHF &	Ultra High Frequency \\
UML & Unified Modelling Language\\
USCGA &	United States Coast Guard Academy\\
VLEO &	Very Low Earth Orbit\\
WFF &	Wallops Flight Facility 
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{mdpi-manuscript-references}

%=====================================
% References, variant B: internal bibliography
%=====================================
\include{references}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2023-04-17 manuscript/buildDocs.sh

@@ -1,0 +1,61 @@
+#!/usr/bin/env bash
+################################################################
+# Build script for building unified model, architecture (spec doc), AIAA manuscript, & assembly instructions in dist/
+################################################################
+
+#### set environment variable for project root ####
+project_root=$PWD
+
+#### convert bib references to yaml to bibtex ####
+# clitool="jinja2"
+# cmdargs="-o references.tex --format yaml references.tex.jinja2 references.yaml"
+# workdir=$project_root
+# cmd="$clitool $cmdargs"
+# podmancmd="podman run --rm -v $workdir:/work -w /work docker.io/roquie/docker-jinja2-cli $cmdargs"
+# condition="$clitool --version | grep 'v0.8.2'"
+
+# if ! eval $condition; then
+#     echo "Generating LaTeX references via podman"
+#     cd $project_root
+#     eval $(echo $podmancmd)
+# else
+#     echo "Generating LaTeX references"
+#     cd $workdir
+#     eval $cmd
+#     cd $project_root
+# fi
+
+#### generate example manuscript ####
+# https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
+cmd="pdflatex template.tex && bibtex template.aux"
+workdir=$project_root/
+podmancmd="podman run --rm -v $workdir:/srv -w /srv docker.io/nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
+
+if [ ! $(pdflatex -version | grep '3.14159265') ] && [ ! $(bibtex -version | grep '0.99d') ]; then
+    echo $(pdflatex -version)
+    echo $(bibtex -version)
+    echo "Pre-Processing LaTeX document with BibTeX of example manuscript via podman..."
+    cd $project_root
+    eval $(echo $podmancmd)
+else
+    echo "Pre-Processing LaTeX document with BibTeX of example manuscript..."
+    cd $workdir
+    eval $cmd
+    cd $project_root
+fi
+
+# https://tex.stackexchange.com/questions/43325/citations-not-showing-up-in-text-and-bibliography
+cmd="pdflatex template.tex && pdflatex template.tex"
+workdir=$project_root/
+podmancmd="podman run --rm -v $workdir:/srv -w /srv docker.io/nanozoo/pdflatex:3.14159265--f2f4a3f bash -c '$cmd'"
+
[…]

### 2023-04-17 manuscript/template.tex
Add images and change image references file path in template.tex

@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/cubesat_family.png}
+    \includegraphics[width=10.5 cm]{assets/cubesat_family.png}
     \caption{CubeSat family by size \cite{cds_rev14}}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/cubesat_blownup.png}
+    \includegraphics[width=10.5 cm]{assets/cubesat_blownup.png}
     \caption{Blownup SeaLion CubeSat Prototype}
@@
 \begin{figure}[H]
-    \includegraphics{Definitions/impedence.png}
+    \includegraphics{assets/impedence.png}
     \caption{Impedence Probe}
@@
 \begin{figure}[H]
-    \includegraphics{Definitions/spectral.png}
+    \includegraphics{assets/spectral.png}
     \caption{Me-S 'Pixel Sensor'}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/decs.png}
+    \includegraphics[width=10.5 cm]{assets/decs.png}
     \caption{DeCS as the black popout booms}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/launch_data.png}
+    \includegraphics[width=10.5 cm]{assets/launch_data.png}
     \caption{Nanosatellite launch data provided by M. Swartwout as of July 21, 2021 \cite{swartwout_data}}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/mission_status.png}
+    \includegraphics[width=10.5 cm]{assets/mission_status.png}
     \caption{Mission status of CubeSat university-class missions provided by Swartwout}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/user_story.png}
+    \includegraphics[width=10.5 cm]{assets/user_story.png}
     \caption{Example YAML file}
@@
 \begin{figure}[H]
-    \includegraphics{Definitions/folders.png}
+    \includegraphics{assets/folders.png}
     \caption{Folder structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/reference.png}
+    \includegraphics[width=10.5 cm]{assets/reference.png}
     \caption{References YAML file}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/reference_file.png}
+    \includegraphics[width=10.5 cm]{assets/reference_file.png}
     \caption{References file structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/stakeholder.png}
+    \includegraphics[width=10.5 cm]{assets/stakeholder.png}
     \caption{Stakeholder YAML file}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/stakeholder_file.png}
+    \includegraphics[width=10.5 cm]{assets/stakeholder_file.png}
     \caption{Stakeholders file structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/uml_stakeholder.png}
+    \includegraphics[width=10.5 cm]{assets/uml_stakeholder.png}
     \caption{Stakeholder UML Diagram}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/userstory_file.png}
+    \includegraphics[width=10.5 cm]{assets/userstory_file.png}
     \caption{User stories file structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/view_beacon.png}
+    \includegraphics[width=10.5 cm]{assets/view_beacon.png}
     \caption{View Beacon YAML structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/uml_userstory.png}
+    \includegraphics[width=10.5 cm]{assets/uml_userstory.png}
     \caption{UML diagram of user stories}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/uml_userstory2.png}
+    \includegraphics[width=10.5 cm]{assets/uml_userstory2.png}
     \caption{UML diagram of ground station operator}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/datastructure.png}
+    \includegraphics[width=10.5 cm]{assets/datastructure.png}
     \caption{Satellite Health Data Structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/datastructure_file.png}
+    \includegraphics[width=10.5 cm]{assets/datastructure_file.png}
     \caption{Data structure File Structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/uml_datastructure.png}
+    \includegraphics[width=10.5 cm]{assets/uml_datastructure.png}
     \caption{UML Diagram of Data Structures}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/components_file.png}
+    \includegraphics[width=10.5 cm]{assets/components_file.png}
     \caption{Components Folder File Structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/components.png}
+    \includegraphics[width=10.5 cm]{assets/components.png}
     \caption{Component YAML File}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{Definitions/N2.png}
+    \includegraphics[width=10.5 cm]{assets/N2.png}
     \caption{N2 Chart Example}

### 2023-04-24 manuscript/references.tex
Address peer comments and MDPI comments in manuscript

@@
     \bibitem{sealion_page}Team, S. SeaLion Mission Architecture. (Old Dominion University,2023), https://odu-cga-cubesat.github.io/sealion-mission-architecture/
+    \bibitem{linkml}Mungall, C. LinkML model your data. {\em LinkML}., https://linkml.io/
+    \bibitem{younse_cameron_bradley_2021}Younse, P., Cameron, J.
+\& Bradley, T.
+Comparative analysis of model-based and traditional systems engineering approaches for architecting a robotic space system through Automatic Information Transfer.
+{\em IEEE Access}.
+\textbf{9} pp.
+107476-107492 (2021)
+    \bibitem{call_herber_2022}Call, D.
+\& Herber, D.
+Applicability of the diffusion of innovation theory to accelerate model-based systems engineering adoption.
+{\em Systems Engineering}.
+\textbf{25}, 574-583 (2022)
+    \bibitem{mazzini}Mazzini, S., Tronci, E., Paccagnini, C.
+\& Olive, X.
+A Model-Based methodology to support the Space System Engineering (MBSSE).
+{\em ERTS2 2010, Embedded Real Time Software \& Systems}.
+(2010,5), https://hal.science/hal-02267836
+    \bibitem{esa}ESA Model-based system engineering. , https://www.esa.int/Enabling\_Support/Preparing\_for\_the\_Future/Discovery\_and\_Preparation/Model-based\_system\_engineering
+    \bibitem{nottage_corns_2012}Nottage, D.
+\& Corns, S.
+Application of model-based systems engineering on a university satellite design team.
+{\em Procedia Computer Science}.
+\textbf{8} pp.
+207-213 (2012)
+    \bibitem{kaslow}Kaslow, D., Ayres, B., Cahill, P., Hart, L.
+\& Yntema, R.
+Developing a CubeSat Model-Based System Engineering (MBSE) reference model — Interim status \#3.
+{\em 2017 IEEE Aerospace Conference}.
+pp.
+1-15 (2017)
+    \bibitem{structurizr}Structurizr Software architecture models as code. {\em Structurizr}., https://structurizr.org/
+    \bibitem{f_prime_prime}Bocchino, R., Levison, J. \& Starch, M. FPP: A Modeling Language for F Prime. {\em 2022 IEEE Aerospace Conference (AERO)}. pp. 1-15 (2022)
+    \bibitem{f_prime}NASA F' a flight software and embedded systems framework. {\em F'}., https://nasa.github.io/fprime/
 \end{thebibliography}

### 2023-04-24 manuscript/template.tex
Address peer comments and MDPI comments in manuscript

@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Kevin Chiu, Sean Marquez and Sharanabasaweshwara Asundi}
+\AuthorNames{Kevin Chiu, Sean Marquez, and Sharanabasaweshwara Asundi}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{The SeaLion flight architecture team for the SeaLion CubeSat project used a model based system engineering with docs-as-code approach to improve planning and organization of the project.
-This was done in response to the growing number of University CubeSat teams with untrained students and personnel.
-The team created tools for the systems architecture with the Mach 30 Modeling Language to create a architecture that is easy to learn and use even for newly admitted team members with little to no training.
-These tools can also generate documents via its own code for easy presentaton on a local file system without any proprietary software.}
+\abstract{The SeaLion mission architecture team sought to create a model based systems engineering approach to assist improving CubeSat success rates as well as for the SeaLion CubeSat project to guide an implementation for the flight software.
+Especially as university CubeSat teams grow in number but are characterized with having untrained students as their core personnel.
+This was done using a document-as-code, or docs-as-code, approach.
+With this the team created tools for the systems architecture with the Mach 30 Modeling Language to create a architecture that is easy to learn and use even for newly admitted team members with little to no training.
+These tools generate documents via its own code for easy presentaton on a local file system without any proprietary software while keeping model content format-agnostic.}
 
@@
 This includes the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, and implementation of the SeaLion mission architecture for the flight software using a model-based approach.
-Through, model-based systems engineering (MBSE), the SeaLion flight software team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.
+Through, model-based systems engineering (MBSE), the SeaLion mission architecture team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.
 These models were used to conduct activities such as design, specification, analysis, verification and validation of the system.
 This was done by applying the NASA handbook on systems engineering \cite{nasa_handbook} to CubeSat mission design in efforts to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.
+The approach presented herein had additional intents to make it was as simple and easy to use as possible.
+This was done by a filesystem-based modelling language that adheres to expected patterns in agile software engineering (i.e., elements for stakeholder needs, user stories, data structures, etc.) using a lightweight YAML-based syntax.
+This article also serves as an expansion of the conference proceedings (copyright held by Kevin Chiu and Sean Marquez) presented at American Institute of Aeronautics and Astronautics (AIAA) SciTech Forum 2023 \cite{scitech_proceeding}.
 
@@
 This greatly decreases the cost of launching a CubeSat which greatly increases the accessibility of inserting objects into space.
+As such, low budget groups such as universities have gravitated towards their use with increasing numbers \cite{swartwout_data}.
+However, this presents challenges since many of the developers in universities are completely new to spacecraft development or systems engineering in general.
 
@@
 
-The SeaLion flight software team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team.
-Three separate payloads require care and attention to ensure success.
-The results of this effort are presented in this article.
+The mission scope of having three payloads require special care and attention to ensure success of the mission.
+However, many of the SeaLion project team members are new to spacecraft development and systems engineering.
+Thus, the SeaLion mission architecture team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team, to guide an implementation for the flight software, and to facilitate interface and assembly documentation.
 
@@
 
-To address some of these issues, the SeaLion flight software team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.
+To address some of these issues, the SeaLion mission architecture team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.
 These provided system engineering approaches and tools include factors such as planning, documentation, project management, and simplifying the process.
@@
 
-A MBSE approach was adopted by the Sealion CubeSat flight software team since it provided benefits such as reducing the ambiguity that usually comes with using informal language to specify systems or its various aspects.
+A MBSE approach was adopted by the Sealion CubeSat mission architecture team since it provided benefits such as reducing the ambiguity that usually comes with using informal language to specify systems or its various aspects.
 It also minimized the duplication of content that tends to accumulate in a document-based system engineering approach.
@@
 Refer to table \ref{tab:language} for modelling language down selection overview.
-In addition, the Sealion CubeSat flight software team eventually decided to adopt a docs-as-code approach to further enhance the MBSE approach to achieve the listed goals shown above.
+In addition, the Sealion CubeSat mission architecture team eventually decided to adopt a docs-as-code approach to further enhance the MBSE approach to achieve the listed goals shown above.
 
@@
 These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.
+Document-based approaches can exacerbate problems since it lacks point-to-point communication channels as well as lacking methods to enforce consistency \cite{call_herber_2022}.
 
 In contrast, a MBSE approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.
-Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:
+MBSE solves the afformentioned issues with document-based approaches by providing models that have direct lines of communication to enforce that consistency.
+Models providing the following key advantages over document-based approaches \cite{ibm_mbse}:
 
@@
 
-\subsection{Docs-As-Code Approach}
-Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.
+As an example of the efficiency gains that MBSE can achieve with a side-by-side comparison between MBSE and non-MBSE approaches.
+Using an architecting process, of 4,858 information element transfers, noted that all of these transfers were done manually with non-MBSE approaches; however, 13\% of these transfers with automated with MBSE with the potential of up to 81\% should it be used for trade study and peer review tasks \cite{younse_cameron_bradley_2021}.
+The SeaLion mission architecture team seeks to take advantage of these efficiency gains that MBSE can achieve.
+Usage of MBSE for space-related projects is not without precedent either.
+Projects have been taking advantage of MBSE such as the ExoMars mission, Euclid, Galileo, and nanosatellite programs \cite{mazzini}, \cite{esa}, \cite{nottage_corns_2012}.
+CubeSat projects have also been using MBSE and have shown to “hold promise of reducing the burden of system engineering tasks” and can “promote uniformity and consistency across future CubeSat models” \cite{kaslow}.
+These attributes are important to reduce workload amongst team members and also to facilitate new team members as they join future projects.
+Especially useful for universities since students are not available long term due to events such as graduation.
+
+\subsection{Documents-As-Code Approach}
+Documents-as-code (Docs-as-code) refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.
 This allows for documentation to updated seamlessly without additional work with document tools (doctools).
-The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio), etc.
+The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio Code), etc.
 To do so would mean that the “following the same workflows as development teams, and being integrated in the product team.
@@
 Proprietary services are not required to generate documentation, modify documentation, or modify models.
+Similar approaches have been seen as Structurizr \cite{structurizr} and F Prime Prime (FPP) \cite{f_prime_prime}.
+FPP is based on F Prime which is an open-source software framework developed by NASA's Jet Propulsion Laboratory \cite{f_prime}.
+While docs-as-code has precedent, the methodologies noted are not easily accesible to those without a sufficient background in programming.
 
@@
 \section{Modelling Language and Methodology}
-The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the flight software team conducting a trade study to determine the most suitable.
-The down selection criteria that the SeaLion CubeSat flight software team has taken into consideration is shown in table \ref{tab:language}.
+The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the mission architecture team conducting a trade study to determine the most suitable.
+The down selection criteria that the SeaLion CubeSat mission architecture team has taken into consideration is shown in table \ref{tab:language}.
 
@@
 OML is a tool to improve the speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.
+However, more recently M30ML's development has been moved from OML to LinkML since it uses a lighter weight toolchain and YAML-based syntax \cite{linkml}.
 
@@
 Whether it be diagrams, tables, or text, continuous updating is ensured that any changes affecting dependencies within the mission architecture are kept in sync.
+YAML files are automatically processed using templates langauge (e.g., Jinja2) via a build shell script.
+This also means that content of the model and formatting of documents are decoupled.
+The model is formatting-agnostic for documentation purposes as this is handled by template language.
 A conference proceeding manuscript presented in AIAA SciTech 2023 was created purely by a docs-as-code format \cite{scitech_proceeding}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Component Implementation}
-The implementation of M30ML for components is still a work in progress at the time of this article's publication.
+\section{M30ML Extensions for Component Implementation}
+The implementation of M30ML for components, at the time of this article's publication, is currently in-process of integrating content information into the model.
 A brief description of current component implementation into the SeaLion model is provided.
-However, many of the implementation methods mentioned herein are subjected to change and are not finalized unlike the architecture described in the prior section.
+However, the model content mentioned herein is subjected to change.
 
 \subsection{Distributed OSHW Framework}
-The M30ML pillars are based on Open Source Hardware (OSHW) principals \cite{mach30_git}.
   The current SeaLion mission architecture repository, at time of article publication, for components is “structured as a Distributed OSHW Framework (DOF) - component for defining the contents of the Mission concept of operations (ConOps) as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs) and assembly instructions for the SeaLion CubeSat” \cite{sealion_mission_architecture}.
-Inside the components folder of the SeaLion mission architecture repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.
+The DOF pillars are based on Open Source Hardware (OSHW) principals \cite{mach30_git}.
+The implementation methodology presented herein is an extension of M30ML specifically for the use of modelling a CubeSat design.
+
+  The SeaLion mission architecture repostiory has a components folder dedicated to its namesake.
+Inside the components folder of the repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.
 Each of those folders would contain a components folder and subsequently those individual labeled components can have their own components folder.
@@
 \section{Conclusion}
-The SeaLion flight software team used MBSE with docs-as-code approach to the SeaLion project.
+The SeaLion mission architecture team used MBSE with docs-as-code approach to the SeaLion project.
 This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for the CubeSat developers.
@@
 Thus, minimal training is required for usage.
-It can also generate documents for easy presentation as well.Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.
+It can also generate documents for easy presentation as well.
+Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.
 

### 2023-04-24 manuscript/template.tex
Incorporate peer comments. Corrected references and citations and resized figures.

@@
 \subsection{Documents-As-Code Approach}
-Documents-as-code (Docs-as-code) refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.
+Documents-as-code (Docs-as-code) refers to a philosophy that team members should be writing documentation with the same tools as code \cite{docs_as_code}.
 This allows for documentation to updated seamlessly without additional work with document tools (doctools).
@@
 To do so would mean that the “following the same workflows as development teams, and being integrated in the product team.
-It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{ibm_mbse}.
-The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{ibm_mbse}.
+It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{docs_as_code}.
+The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{docs_as_code}.
 In addition, these models can stored and used persistently on a local file system without the use of cloud based services.
@@
 Similar approaches have been seen as Structurizr \cite{structurizr} and F Prime Prime (FPP) \cite{f_prime_prime}.
-FPP is based on F Prime which is an open-source software framework developed by NASA's Jet Propulsion Laboratory \cite{f_prime}.
+FPP is based on F Prime which is an open-source software framework developed by NASA's Jet Propulsion Laboratory \cite{f_prime}; it is a model-driven approach for producing flight software code that can be compiled directly onto flight hardware.
 While docs-as-code has precedent, the methodologies noted are not easily accesible to those without a sufficient background in programming.
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/user_story.png}
+    \includegraphics[width=12 cm]{assets/user_story.png}
     \caption{Example YAML file}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/reference.png}
+    \includegraphics[width=10 cm]{assets/reference.png}
     \caption{References YAML file}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/uml_stakeholder.png}
+    \includegraphics[width=12 cm]{assets/uml_stakeholder.png}
     \caption{Stakeholder UML Diagram}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/uml_userstory.png}
+    \includegraphics[width=12 cm]{assets/uml_userstory.png}
     \caption{UML diagram of user stories}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/uml_userstory2.png}
+    \includegraphics[width=12 cm]{assets/uml_userstory2.png}
     \caption{UML diagram of ground station operator}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/datastructure.png}
+    \includegraphics[width=12 cm]{assets/datastructure.png}
     \caption{Satellite Health Data Structure}
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/uml_datastructure.png}
+    \includegraphics[width=12 cm]{assets/uml_datastructure.png}
     \caption{UML Diagram of Data Structures}
@@
 Many of the figures are UML diagrams that are auto-generated artifacts rendered from the M30ML modeling language and formatted using the Liquid template language.
-This is the link for the docs-as-code approach.
+This is how the docs-as-code approach is implemented.
 YAML code files are used to generate documents for information sharing between group members.
@@
 This also means that content of the model and formatting of documents are decoupled.
-The model is formatting-agnostic for documentation purposes as this is handled by template language.
+The model is formatting-agnostic for documentation purposes as this is handled by the template language.
 A conference proceeding manuscript presented in AIAA SciTech 2023 was created purely by a docs-as-code format \cite{scitech_proceeding}.
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/components.png}
+    \includegraphics[width=5 cm]{assets/components.png}
     \caption{Component YAML File}
@@
 
-\acknowledgments{Special thanks to Dr. Sharan Asundi, PhD., Sean Marquez, and the SeaLion Project Team}
+\acknowledgments{Special thanks to the SeaLion Project Team}
 
@@
 EVR &	Event\\
+FPP &	F Prime Prime\\
 GPS &	Global Positioning System\\

### 2023-05-30 manuscript/template.tex

@@
 Through, model-based systems engineering (MBSE), the SeaLion mission architecture team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.
-These models were used to conduct activities such as design, specification, analysis, verification and validation of the system.
+These models were used to conduct activities such as design, specification, analysis, verification, and validation of the system.
 This was done by applying the NASA handbook on systems engineering \cite{nasa_handbook} to CubeSat mission design in efforts to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.
-The approach presented herein had additional intents to make it was as simple and easy to use as possible.
+The approach presented herein had additional intents to make it as simple and easy to use as possible.
 This was done by a filesystem-based modelling language that adheres to expected patterns in agile software engineering (i.e., elements for stakeholder needs, user stories, data structures, etc.) using a lightweight YAML-based syntax.
@@
 \subsection{CubeSat}
-The CubeSat, originating from California Polytechnic State University in 1999, are a standardized form of nanosatellites.
+The CubeSat, originating from California Polytechnic State University in 1999, is a standardized form of nanosatellites.
 Nanosatellites are satellites typically defined with a mass of less than 10 kg.
-CubeSats, also known as Cube Satellites, are defined by the standardized and modular architecture of 1-Unit (1U) cube with dimensions of 10 cm X 10 cm X 10 cm with a mass of up to 2 kg \cite{cds_rev14}.
+CubeSats, also known as Cube Satellites, are defined by the standardized and modular architecture of a 1-Unit (1U) cube with dimensions of 10 cm X 10 cm X 10 cm with a mass of up to 2 kg \cite{cds_rev14}.
 They can be scaled to 2-Units (2U), 3-Units (3U), or higher depending on units added as shown in figure \ref{fig:cubesat_family} with sizes designated by the CubeSat specification \cite{cds_rev14}.
-This is done by the additional of standardized cube units to upscale the CubeSat.
+This is done by the addition of standardized cube units to upscale the CubeSat.
 The ability to scale by modularity gives a highly standardized structure for ease of expansion to provide versatility in functionality.
 Due to their small size, mass, and lack of dedicated launch vehicles, CubeSats are typically launched as secondary payloads in conjunction with other larger satellites, informally known as “piggy-backing”.
-This greatly decreases the cost of launching a CubeSat which greatly increases the accessibility of inserting objects into space.
-As such, low budget groups such as universities have gravitated towards their use with increasing numbers \cite{swartwout_data}.
+This greatly decreases the cost of launching a CubeSat which increases the accessibility of inserting objects into space.
+As such, low budget groups such as universities have gravitated towards CubeSats with increasing numbers \cite{swartwout_data}.
 However, this presents challenges since many of the developers in universities are completely new to spacecraft development or systems engineering in general.
@@
 The prototype CubeSat model is shown in figure \ref{fig:cubesat_blowup}.
-The intended mission profile was to have an no-orbit time for mere days due to its planned very low earth orbit (VLEO) altitude.
+The intended mission profile was to have an on-orbit time for mere days due to its planned very low earth orbit (VLEO) altitude.
 Thus, SeaLion was to complete validation of its payloads before either power is lost in its non-rechargeable batteries or the satellite reenters and burns up in Earth's atmosphere.
 The predicted on-orbit time was 10 days.
-However, weight considerations on the planned Antares caused SeaLion to be moved to a Q4 launch on a Firefly rocket from Vandenberg Space Force Base into a sun synchronous orbit, of 500 miles altitude.
+However, mass considerations on the planned Antares rocket caused SeaLion to be moved to a Q4 2023 launch on a Firefly rocket from Vandenberg Space Force Base into a sun synchronous orbit, of 500 miles altitude.
 The content presented in this article is based on the prior mission profile from the launch at WFF into VLEO.
@@
 
-The payloads are as follows.
-The first payload is provided by the USCGA and AFIT, is the Impedance Probe (IP).
+The first payload, provided by the USCGA and AFIT, is the Impedance Probe (IP).
 The IP is derived from U.S.
-Naval Research Laboratory's (NRL's) 'Space PlasmADiagnostic suitE' (SPADE) aboard NASA's International Space Station (ISS) where plasma density and temp are computed with alternating current (AC) impedance measurements using an innovative, first of its kind surface mounted dipole radio frequency antenna \cite{sealion_cdr}.
+Naval Research Laboratory's (NRL's) 'Space PlasmADiagnostic suitE' (SPADE) aboard NASA's International Space Station (ISS) where plasma density and temperature are computed with alternating current (AC) impedance measurements using an innovative, first of its kind surface mounted dipole radio frequency antenna \cite{sealion_cdr}.
 The IP part is shown in figure \ref{fig:IP}.
@@
 \begin{figure}[H]
-    \includegraphics{assets/impedence.png}
+    \includegraphics[width=13.75 cm]{assets/impedence.png}
     \caption{Impedence Probe}
@@
 
-The second payload, provided by the USCGA and AFIT, is the multispectral (Me-S) 'Pixel Sensor' with a with a 450 nm - 1000 nm spectral range \cite{sealion_cdr}.
+The second payload, provided by the USCGA and AFIT, is the multispectral (Me-S) 'Pixel Sensor' with a 450 nm - 1000 nm spectral range \cite{sealion_cdr}.
 Its purpose is to provide SeaLion's in-situ spectral data as a baseline.
@@
 The third payload, provided by ODU, is the deployable composite structure (DeCS).
-This payload is a proof-of-concept deployable mechanism and composite boom that is meant to be a platform host to a number of number of applications \cite{sealion_cdr}.
+This payload is a proof-of-concept deployable mechanism and composite boom that is meant to be a platform host of a number of applications \cite{sealion_cdr}.
 For example, these applications include solar panels, solar sails, drag sails, sensory sails, and magnetometer booms.
-Deployment on SeaLion is meant to validate the deployable mechanism for composite boom in the space environment and to validate boom dynamic during and after deployment in orbit.
+Deployment on SeaLion is meant to validate the deployable mechanism for a composite boom in the space environment and to validate boom dynamics during and after deployment in orbit.
 The DeCS upon deployment is shown in figure \ref{fig:DeCS}.
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/decs.png}
+    \includegraphics[width=13.75 cm]{assets/decs.png}
     \caption{DeCS as the black popout booms}
@@
 
-The mission scope of having three payloads require special care and attention to ensure success of the mission.
+The mission scope with three payloads requires special care and attention to ensure success of the mission.
 However, many of the SeaLion project team members are new to spacecraft development and systems engineering.
-Thus, the SeaLion mission architecture team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team, to guide an implementation for the flight software, and to facilitate interface and assembly documentation.
+In response, experienced team members took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team, to guide an implementation for the flight software, and to facilitate interface and assembly documentation.
 
@@
 CubeSats were initially conceived as educational tools for space systems engineering \cite{heidt_new}.
-Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the aforementioned low cost of production and launch of these CubeSat satellites.
-As such, there has been increasing popularity for CubeSats as seen by the number of launches in figure \ref{fig:launch_data} since year 2000 \cite{swartwout_data} apart from the notable exceptions in the years 2020 and 2021; the author speculates that this downturn is due to the COVID-19 pandemic.
+Now, their roles have been expanded to not only just educational tools but for observation, technology demonstrations, and research that were previous monopolized by much larger satellites due to the low cost of production and launch of these CubeSats.
+As such, there has been increasing popularity for CubeSats as seen by the number of launches in figure \ref{fig:launch_data} since the year 2000 \cite{swartwout_data} apart from the notable exceptions in the years 2020 and 2021; the author speculates that this downturn is due to the COVID-19 pandemic.
 The CubeSat design specification \cite{cds_rev14} as well as the availability of commercial off-the-shelf (COTS) parts and kits have greatly influenced the rise of popularity.
-For example, a basic CubeSat kit from Pumpkin can be purchased with a baseline price of as little as 6250 US dollars \cite{pumpkin_cubesat}.
-Even the SeaLion CubeSat utilizes many COTS parts as well.
-Thus, it has become highly accessible to low-budget groups such as small companies and university groups.
-CubeSats have caused the “democratization” of space due to their low cost which has allowed many groups to fly satellites \cite{cubesat_handbook}.
+For example, a basic CubeSat kit from a space systems company such as Pumpkin can be purchased with a baseline price of as little as 6250 US dollars \cite{pumpkin_cubesat}.
+The SeaLion CubeSat also utilizes many COTS parts as well.
+Thus, CubeSats have become highly accessible to low-budget groups such as small companies and university groups.
+CubeSats have caused the “democratization” of space by allowing many groups to fly satellites \cite{cubesat_handbook}.
 
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/launch_data.png}
+    \includegraphics[width=13.75 cm]{assets/launch_data.png}
     \caption{Nanosatellite launch data provided by M. Swartwout as of July 21, 2021 \cite{swartwout_data}}
@@
 This showcases directly how many university-based CubeSat projects occurred or potentially may occur if trends continue onwards into the future.
-However, this poses challenges to many of these projects given the mainly student composed teams which includes the SeaLion mission at ODU.
+However, this presents its own challenges.
 
 \subsection{Ensuring CubeSat Success}
-The increased number of CubeSats launched also means a greater number of CubeSats from universities being launched as well.
-The motivation of this article is to improve the success rate of CubeSat missions from university groups by providing readily available and easily usable tools for university teams.
+The motivation of this article is to improve the success rate of CubeSat missions from university groups by providing readily available and usable tools for university teams.
 To further reinforce the need to improve the success rate, the following data is presented in figure \ref{fig:mission_status} which showcases the total successes and failures of CubeSats from universities for the given time periods \cite{reliving_24}.
-The data provided is categorized by six different mission statuses of unknown, launch fail, dead on arrival (DOA), early loss, partial mission, and full mission.
+The data provided is categorized by six different mission success statuses of unknown, launch fail, dead on arrival (DOA), early loss, partial mission, and full mission.
 
@@
     \includegraphics[width=10.5 cm]{assets/mission_status.png}
-    \caption{Mission status of CubeSat university-class missions provided by Swartwout}
+    \caption{Mission status of CubeSat university-class missions provided by Swartwout \cite{reliving_24}}
 	\label{fig:mission_status}
@@
 
-As seen in the preceding figure \ref{fig:mission_status}, failure rates over time appear to be increasing among CubeSats launched from universities.
-However, Swartwout notes that highest number of the failures originate from “regular independent” groups with a failure rate of 65 percent at the time of data gathering in 2017 \cite{reliving_24}.
-These “regular independent” groups are groups that have fewer than four missions nor designated as a national center of for spacecraft development by its government.
+As seen in the preceding figure \ref{fig:mission_status}, university CubeSat mission failure rates have increased while partial and full mission success rates have decreased in conjunction with the increasing number of missions as seen in figure \ref{fig:launch_data}.
+However, Swartwout notes that the highest number of failures originate from “regular independent” groups with a failure rate of 65 percent at the time of data gathering in 2017 \cite{reliving_24}.
+These “regular independent” groups have fewer than four missions performed nor are designated as a national center for spacecraft development by its government.
 
 The issue present is that many of the growing number of university groups producing CubeSats lack the resources, training, experience, or methodology to reliably give assurance to their missions.
-Often, the majority of the work is done by untrained university students that are, many times, unfamiliar with the system engineering, design methodologies, testing, etc.
-that are associated with CubeSat development.
+The majority of the work is often done by untrained students that are unfamiliar with the aspects of CubeSat development (e.g., system engineering, design methods, and testing).
 The SeaLion team also faced these issues as well.
 
-To address some of these issues, the SeaLion mission architecture team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.
-These provided system engineering approaches and tools include factors such as planning, documentation, project management, and simplifying the process.
-Special attention should be given to systems engineering and information exchange for multidisciplinary teams \cite{aalto}.
-To showcase these factor's importance, a survey conducted, by University of Bristol, on how to set up CubeSat projects of forty CubeSat groups emphasized the following relevant lessons learned \cite{howtosetup}:
+To address some of these issues, SeaLion team members sought to simplify the development process by providing readily available and learnable system engineering approaches and tools.
+These provided approaches and tools include factors such as planning, documentation, project management, and simplifying the process.
+This is important since special attention should be given to systems engineering and information exchange for multidisciplinary teams \cite{aalto}.
+To showcase these factor's importance, a survey of forty CubeSat groups on how to set up CubeSat projects, conducted by the University of Bristol, emphasized the following relevant lessons learned \cite{howtosetup}:
 
@@
 	\item	Documentation / Project Management: Groups should have “good documentation of requirements, work done and work to do”.;
-	\item	Simplicity: Simply anything you possibly can to increase confidence in success.
+	\item	Simplicity: Simplify anything you possibly can to increase confidence in success.
 \end{itemize}
@@
 The goal of the SeaLion CubeSat mission architecture was to capture the data structures and expected behaviors for the development of the flight software.
-It has to be done such that it can unambiguously understood well enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.
+The data structures and expected behaviors were captured in such a way that can unambiguously understood well enough to be implemented, as well as provide full traceability and rationale for architectural elements with minimal configuration management overhead \cite{sealion_mission_architecture}.
 Thus, the SeaLion CubeSat mission architecture had to achieve the following:
@@
 	\item 	Documents should be in plaintext as to be compatible with modern distributed version control system (e.g., Git) and for ease of use.;
-	\item 	Documents should be able to sit alongside code and speak to one another.;
+	\item 	Documents should be able to persist alongside code and communicate to one another.;
 	\item 	Documents should be model-based as to have a separation of concerns between content and formatting as well as be both human and machine-readable for querying and generating views.;
@@
 
-Proper adoption of a MBSE approach also includes the selection of modeling language and modeling tool.
+Proper adoption of a MBSE approach also includes the selection of the modeling language and modeling tool.
 Considerations when selecting the modeling language and tool was overhead incurred from training the team, the technical overhead of setting up modelling tools, and future adaptability.
@@
 \subsection{Model-Based Systems Engineering}
-As noted prior that attention should be given to as planning, documentation, project management, and simplifying the process.
-That special emphasize should be given to systems engineering and information exchange \cite{aalto}.
+As noted prior that attention should be given for planning, documentation, project management, and simplifying the process.
+Special emphasize should be given to systems engineering and information exchange \cite{aalto}.
 
 Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.
-Information in a traditional systems engineering approach today is mostly captured informally, not authored based on a methodology, configuration managed in silo tools, adhocly and infrequently integrated, not easily traceable to its provenance, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.
+Information in a traditional systems engineering approach today is mostly captured informally.
+For example, it incurs disadvantages such as information not being authored based on a methodology, adhocly and infrequently integrated, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.
 These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.
@@
 
-In contrast, a MBSE approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.
-MBSE solves the afformentioned issues with document-based approaches by providing models that have direct lines of communication to enforce that consistency.
-Models providing the following key advantages over document-based approaches \cite{ibm_mbse}:
+In contrast, a MBSE approach captures information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.
+Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:
 
 \begin{itemize}
-	\item	Information is readily communicated and shared within the project.;
-	\item	Changes are easily accommodated.;
+	\item	Information is readily communicated and shared within the project.
+	\item	Changes are easily accommodated.
 	\item	Traceability is automated.
@@
 
-As an example of the efficiency gains that MBSE can achieve with a side-by-side comparison between MBSE and non-MBSE approaches.
-Using an architecting process, of 4,858 information element transfers, noted that all of these transfers were done manually with non-MBSE approaches; however, 13\% of these transfers with automated with MBSE with the potential of up to 81\% should it be used for trade study and peer review tasks \cite{younse_cameron_bradley_2021}.
+To showcase the benefits, an architecting process of 4,858 information element transfers was performed.
+It noted that all of these transfers were done manually with non-MBSE approaches; however, 13\% of these transfers were automated with MBSE with the potential of up to 81\% should it be used for trade study and peer review tasks \cite{younse_cameron_bradley_2021}.
 The SeaLion mission architecture team seeks to take advantage of these efficiency gains that MBSE can achieve.
-Usage of MBSE for space-related projects is not without precedent either.
-Projects have been taking advantage of MBSE such as the ExoMars mission, Euclid, Galileo, and nanosatellite programs \cite{mazzini}, \cite{esa}, \cite{nottage_corns_2012}.
-CubeSat projects have also been using MBSE and have shown to “hold promise of reducing the burden of system engineering tasks” and can “promote uniformity and consistency across future CubeSat models” \cite{kaslow}.
-These attributes are important to reduce workload amongst team members and also to facilitate new team members as they join future projects.
-Especially useful for universities since students are not available long term due to events such as graduation.
+Space projects have been taking advantage of MBSE such as the ExoMars mission, Euclid, Galileo, and nanosatellite programs \cite{mazzini}, \cite{esa}, \cite{nottage_corns_2012}.
+CubeSat projects have also been using MBSE and have shown to “hold promise of reducing the burden of system engineering tasks” \cite{kaslow} and can “promote uniformity and consistency across future CubeSat models” \cite{kaslow}.
+These attributes are important to reduce workload amongst team members and to facilitate new team members as they join future projects.
+Facilitation of new members is especially useful for universities since students are not available long term due to events such as graduation.
 
@@
 Documents-as-code (Docs-as-code) refers to a philosophy that team members should be writing documentation with the same tools as code \cite{docs_as_code}.
-This allows for documentation to updated seamlessly without additional work with document tools (doctools).
+This allows for documentation to be updated seamlessly without additional work with document tools (doctools).
 The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio Code), etc.
-To do so would mean that the “following the same workflows as development teams, and being integrated in the product team.
-It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{docs_as_code}.
+To do so would mean that writers would follow the same workflows as the development team and they would be integrated into the product team.
+A stated result would be to enable "a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{docs_as_code}.
 The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{docs_as_code}.
-In addition, these models can stored and used persistently on a local file system without the use of cloud based services.
+In addition, these models can be stored and used persistently on a local file system without the use of cloud based services.
 Proprietary services are not required to generate documentation, modify documentation, or modify models.
-Similar approaches have been seen as Structurizr \cite{structurizr} and F Prime Prime (FPP) \cite{f_prime_prime}.
+Similar approaches have been seen in Structurizr \cite{structurizr} and F Prime Prime (FPP) \cite{f_prime_prime}.
 FPP is based on F Prime which is an open-source software framework developed by NASA's Jet Propulsion Laboratory \cite{f_prime}; it is a model-driven approach for producing flight software code that can be compiled directly onto flight hardware.
@@
 \section{Modelling Language and Methodology}
-The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the mission architecture team conducting a trade study to determine the most suitable.
+The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the mission architecture team conducting a trade study to determine the most suitable one.
 The down selection criteria that the SeaLion CubeSat mission architecture team has taken into consideration is shown in table \ref{tab:language}.
@@
 M30ML was chosen for its lightweight human and machine-readable textual syntax, file-based model interchange support (for persisting models directly on the local filesystem), ability to generate both textual and graphical views, and relatively minimal overhead with modern doctools \cite{mach30_git}.
-The lightweight textual syntax and minimal over head is especially important for for a team that had very minimal experience working with such tools.
+The lightweight textual syntax and minimal overhead is especially important for for a team that has very minimal experience working with such tools.
 Other candidate modelling languages lacked in many regards compared to M30ML in these criteria and thus, M30ML was selected.
 SysML v2 had a good number of characteristics that M30ML had, however, the lack of minimal overhead with modern doctools prevented its adoption.
+At the time of publication of this article, the current state of the art MBSE languages (e.g., SysML v2) have not prescribed an approach for file-based model interchange for persisting models on the local filesystem.
+SysML v1 has XML Metadata Interchange (XMI) as a file-based interchange but it can only handle graphical views and not textual views.
+Adapting other MBSE langauges would take significent work to adopt a docs-as-code approach in their current states.
 
@@
 OML is a language that enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}.
-OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of aforementioned standard for use in systems engineering \cite{oml_language}.
+OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of the aforementioned standard for use in systems engineering \cite{oml_language}.
 OWL2 does not conform easily to individual modelling rules without tooling support; thus, OML was created.
 OML is a tool to improve the speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.
-However, more recently M30ML's development has been moved from OML to LinkML since it uses a lighter weight toolchain and YAML-based syntax \cite{linkml}.
+However, more recently, M30ML's development has been moved from OML to LinkML since it uses a lighter weight toolchain and YAML-based syntax \cite{linkml}.
 
@@
 M30ML is a language for modeling an architecture with YAML-based modeling.
-YAML is especially important as a file structure since it is a highly structured, machine queryable, human-readable, lightweight, and line-oriented markup language.
+YAML as a file type is a highly structured, machine queryable, human-readable, lightweight, and line-oriented markup language.
 This makes it ideal for document generation use cases as well as use with version control tools like Git.
 The simple line by line structure as shown in figure \ref{fig:example_yaml} exemplifies its simplicity.
-Users are easily able to read, interpret, and edit documents using the YAML file format so as long they are taught what each line element is.
-Doctools such as asciidoctor and bibtex were made compatible easily with minimal technical overhead which was taken advantage of for the submission to the AIAA SciTech 2023 Forum \cite{scitech_proceeding}.
+Users are readily able to read, interpret, and edit documents using the YAML file format so as long they are taught what each line element is.
+Doctools such as asciidoctor and bibtex were made compatible with minimal technical overhead which was taken advantage of for the submission to the AIAA SciTech 2023 Forum \cite{scitech_proceeding}.
 M30ML also provided modeling elements familiar in agile software development, such as stakeholder needs, user stories, data structures, and with relationship elements for defining traceability between modeling elements \cite{mach30_git}.
@@
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/user_story.png}
+    \includegraphics[width=13.75 cm]{assets/user_story.png}
     \caption{Example YAML file}
@@
 The SeaLion mission architecture is organized into two main folders of architecture and of components \cite{sealion_mission_architecture}.
-Architecture contains the references, stakeholder needs, user stories, and data structures shown in figure \ref{fig:folders}.
+Architecture contains the references, stakeholder needs, user stories, and data structures shown in figure \ref{fig:reference_file}.
 Components, as the name implies, contains the components and subcomponents of the CubeSat.
 For the focus of this article, the architecture folder is the primary concern.
-Components is currently a work in progress at time of publication of this article and will be addressed with other future required work.
+Components is currently a work in progress at time of publication of this article and will be addressed with future required work.
 For the mission architecture shown in figure \ref{fig:folders}, generally data structures are derived from user stories.
 Further, user stories are subsequently derived from stakeholder needs with their respective references.
-
-\begin{figure}[H]
-    \includegraphics{assets/folders.png}
-    \caption{Folder structure}
-	\label{fig:folders}
-    \end{figure}
-	\noindent   
-\unskip
-
-References are simply stored reference material such as standards, specifications books, etc.
-They are very simple two-line YAML files as shown in figure \ref{fig:reference_yaml}.
-This creates a continued link between the YAML files within their respective folders from which documents can be updated seamlessly.
-Information changed within one file can interact with other files.
-All YAML references files in the mission architecture at the time of article's publication is listed within and figure \ref{fig:reference_file}.
-
-\begin{figure}[H]
-    \includegraphics[width=10 cm]{assets/reference.png}
-    \caption{References YAML file}
-	\label{fig:reference_yaml}
-    \end{figure}   
-\unskip
 
@@
 
+References are simply stored reference material such as standards, specifications books, etc.
+They are very simple two-line YAML files as shown in figure \ref{fig:reference_yaml}.
+This creates a continued link between the YAML files within their respective folders from which documents can be updated seamlessly.
+Information changed within one file can interact with other files.
+All YAML references files in the mission architecture at the time of article's publication is listed within figure \ref{fig:reference_file}.
+
+\begin{figure}[H]
+    \includegraphics[width=13.75 cm]{assets/reference.png}
+    \caption{References YAML file}
+	\label{fig:reference_yaml}
+    \end{figure}   
+\unskip
+
 \subsection{Stakeholder Needs}
@@
 After SeaLion's project methodology documentation is committed to using M30ML based on YAML modelling tools, the first step is to identify all stakeholder needs.
-The two primary stakeholders of SeaLion are ODU and the CGA.
+The two primary stakeholders of SeaLion are ODU and the USCGA.
 Their respective needs are classified from primary, secondary, and tertiary based on mission importance.
 
-Stakeholder YAML files are stored in '1-StakeholderNeeds' shown in figure \ref{fig:folders}.
+Stakeholder YAML files are stored in the '1-StakeholderNeeds' folder shown in figure \ref{fig:folders}.
 Each file is numbered with a X.X number format with the first number designating if it's primary, secondary, or tertiary and the second number denoting a place within a list of that class (e.g., 1.1 would indicate primary stakeholder need 1).
@@
 While not all stakeholder needs have it filled, it is available to be used as needed.
-figure \ref{fig:stakeholder_file} showcases all the YAML files stored in the stakeholders file folder.
+Figure \ref{fig:stakeholder_file} showcases all the YAML files stored in the stakeholders file folder.
 
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/stakeholder.png}
+    \includegraphics[width=13.75 cm]{assets/stakeholder.png}
     \caption{Stakeholder YAML file}
@@
 The generation of these diagrams via the YAML files presented herein showcases the docs-as-code approach.
-YAML files structured as a code are then converted into easily human readable documents for presentation.
+YAML files structured as a code are then converted into human readable documents for presentation.
 
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/uml_stakeholder.png}
+    \includegraphics[width=13.75 cm]{assets/uml_stakeholder.png}
     \caption{Stakeholder UML Diagram}
@@
 These user stories are written from the perspective of the ground operator which would be a student from ODU who monitors and controls the functions of the SeaLion CubeSat.
-User story YAML files are stored in '2-UserStories' folder shown in figure \ref{fig:folders}.
+User story YAML files are stored in the '2-UserStories' folder shown in figure \ref{fig:folders}.
 These files are all given an ID number in no particular order of importance.
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/view_beacon.png}
+    \includegraphics[width=13.75 cm]{assets/view_beacon.png}
     \caption{View Beacon YAML structure}
@@
 
-Figure \ref{fig:uml_userstory} and figure \ref{fig:uml_userstory2} are UML diagrams generated using the YAML files stored in '2-UserStories' folder.
-Figure \ref{fig:uml_userstory} is a mapping of stakeholder needs to user stories.
+Figure \ref{fig:uml_userstory} and figure \ref{fig:uml_userstory2} are UML diagrams generated using the YAML files stored in the '2-UserStories' folder.
+Figure \ref{fig:uml_userstory} is an excerpt of mapping of stakeholder needs to user stories.
 Figure \ref{fig:uml_userstory2} is the user stories presented in a use case diagram to showcase what the ground station operator needs to perform.
 The generation of these diagrams via the YAML files presented herein showcases the docs-as-code approach.
-YAML files structured as a code are then converted into easily human readable documents for presentation.
+YAML files structured as a code are then converted into human readable documents for presentation.
 
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/uml_userstory.png}
-    \caption{UML diagram of user stories}
+    \includegraphics[height=21 cm]{assets/uml_userstory.png}
+    \caption{Excerpt of UML diagram of user stories}
 	\label{fig:uml_userstory}
@@
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/uml_userstory2.png}
+    \includegraphics[width=13.75 cm]{assets/uml_userstory2.png}
     \caption{UML diagram of ground station operator}
@@
 User stories once identified will then lead to design decisions captured in data structures and activity definitions.
-These data structures are the data that would transmitted back and forth between ground station operator and CubeSat.
-Data structure YAML files are stored in '3-DataStructures' folder shown in figure \ref{fig:folders}.
+These data structures are the data that would be transmitted back and forth between ground station operator and CubeSat.
+Data structure YAML files are stored in the '3-DataStructures' folder shown in figure \ref{fig:folders}.
 Each data structure YAML has name, purpose, template, elements, and derived from elements as shown in figure \ref{fig:datastructure} as an example.
@@
 Table \ref{tab:datastructure} is a table generated from the YAML file shown in figure \ref{fig:datastructure} for documentation purposes.
-figure \ref{fig:datastructure_file} details the file structure under the 3-DataStructures' folder.
+Figure \ref{fig:datastructure_file} details the file structure under the 3-DataStructures' folder.
 
@@
 	\toprule
-	\textbf{Field}  & \textbf{Type}  & \textbf{Item Type}  & \textbf{Description}\\
+	\textbf{Field}  & \textbf{Type}  & \textbf{Description}\\
 	\midrule
-	call\_sign           & string         &  & Identifying call sign for the Sealion mission.                                                                         \\ \hline
-	battery\_health      & float          &  & Percent value indicating the remaining charge of the batteries.                                                        \\ \hline
-	temperature\_battery & float          &  & The temperature of the battery. Units in Kelvin.                                                                       \\ \hline
-	mode                 & integer        &  & Integer value indicating current mission mode. 0 = Safe, 1 = mission mode 1, 2 =   mission mode 2, 3 = mission mode 3. \\ \hline
-	state\_vector        & ECIStateVector &  & ECI state vector from orbit propogator at time of beacon. \\    
+	call\_sign           & string         & Identifying call sign for the Sealion mission.                                                                         \\ \hline
+	battery\_health      & float          & Percent value indicating the remaining charge of the batteries.                                                        \\ \hline
+	temperature\_battery & float          & The temperature of the battery. Units in Kelvin.                                                                       \\ \hline
+	mode                 & integer        & Integer value indicating current mission mode. 0 = Safe, 1 = mission mode 1, 2 =   mission mode 2, 3 = mission mode 3. \\ \hline
+	state\_vector        & ECIStateVector & ECI state vector from orbit propogator at time of beacon. \\    
 	\bottomrule
@@
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/datastructure.png}
+    \includegraphics[width=13.75 cm]{assets/datastructure.png}
     \caption{Satellite Health Data Structure}
@@
 Note that this data structure is derived from the user stories 2 and 4.1 described in the prior section detailing user stories.
-These user stories detail the ground station operator's tasks to view the satellite beacon data and to request satellite health data packet so that operator can verify that AODS sensors and GPS data are within nominal parameters.
+These user stories detail the ground station operator's tasks to view the satellite beacon data and to request the satellite health data packet so that the operator can verify that AODS sensors and GPS data are within nominal parameters.
 Table \ref{tab:datastructure} details the various fields that would be required in this beacon data packet to accomplish the aforementioned tasks.
 
-Figure \ref{fig:uml_datastructure} is a UML diagram of mapping of user stories to data structures generated from the YAML file shown in figure \ref{fig:datastructure}.
-The generation of this diagram and the tables via the YAML files presented herein showcases the docs-as-code approach.
-YAML files structured as a code are then converted into easily human readable documents for presentation.
-
 \begin{figure}[H]
-    \includegraphics[width=12 cm]{assets/uml_datastructure.png}
+    \includegraphics[width=13.75 cm]{assets/uml_datastructure.png}
     \caption{UML Diagram of Data Structures}
@@
 \unskip
+
+Figure \ref{fig:uml_datastructure} is a UML diagram of mapping of user stories to data structures generated from the YAML file shown in figure \ref{fig:datastructure}.
+Note that not every data structure is linked to a user story.
+These unlinked data structures are necessary to CubeSat functionality without being linked to the stakeholders and user story chain.
+The generation of this diagram and the tables via the YAML files presented herein showcases the docs-as-code approach.
+YAML files structured as a code are then converted into human readable documents for presentation.
 
@@
 The SeaLion mission architecture repostiory has a components folder dedicated to its namesake.
-Inside the components folder of the repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.
+Inside the components folder of the repository are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.
 Each of those folders would contain a components folder and subsequently those individual labeled components can have their own components folder.
@@
 A series of YAML files for components have been created.
-figure \ref{fig:components} showcases the parts YAML file, however, parts is only one element of the component's data structure thus far.
+Figure \ref{fig:components} showcases the parts YAML file, however, parts is only one element of the component's data structure thus far.
 Showcased in table \ref{tab:component_data} is the entire component data structure from the SeaLion DOF templates \cite{sealion_dof}.
@@
 	\item	Component: Represents the smallest logical element in an OSHW project.
-A Component may be a project in its own right (with a sub-component hierarchy) or may be nested as a sub-component in the "source" of another component.;
-	\item	Component List Item: Identifies a part or tool used in the fabrication of the component. Parts and tools are defined by their source material in the components list.;
-	\item	Activity Step: Defines a single step in an activity, e.g., assembly instructions.;
-	\item	Parameter: Defines a data structure for an input or output of a component function.;
-	\item	Function: Defines a data structure for a component function.;
-	\item	Interface List Item: Identifies an interface on a part or tool.;
+A Component may be a project in its own right (with a sub-component hierarchy) or may be nested as a sub-component in the "source" of another component.
+	\item	Component List Item: Identifies a part or tool used in the fabrication of the component. Parts and tools are defined by their source material in the components list.
+	\item	Activity Step: Defines a single step in an activity (e.g., assembly instructions).
+	\item	Parameter: Defines a data structure for an input or output of a component function.
+	\item	Function: Defines a data structure for a component function.
+	\item	Interface List Item: Identifies an interface on a part or tool.
 \end{itemize}
@@
 These assembly instructions would also be generated through the SeaLion mission architecture repository much akin to other documents for SeaLion.
-Thus, it creates an easily human readable document from the YAML files code as per the docs-as-code approach.
+Thus, it creates a human readable document from the YAML files code as per the docs-as-code approach.
 
-Eventually, the purpose of all these component data structures is to also create an N2 diagram.
-An N2 diagram is used to “is used to capture the interfaces, mechanical and electrical, for all components of the satellite obtained through the mapping process” \cite{asundi13_cubes}.
+Eventually, the purpose of all these component data structures is to also create a N2 diagram.
+A N2 diagram is used to “capture the interfaces, mechanical and electrical, for all components of the satellite obtained through the mapping process” \cite{asundi13_cubes}.
 An example has been provided in figure \ref{fig:N2}.
@@
 Thus, it allows for continuous updating that ensures that any changes affecting dependencies within the mission architecture are kept in sync.
-This would allow for a team to easily identify “areas where conflicts could arise in interfaces, and highlights input and output dependency assumptions and requirements” \cite{asundi13_cubes}.
+This would allow for a team to identify “areas where conflicts could arise in interfaces, and highlights input and output dependency assumptions and requirements” \cite{asundi13_cubes}.
 Thus, leading to higher efficacy in planning the development and assembly of the satellite.
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{assets/N2.png}
+    \includegraphics[width=13.75 cm]{assets/N2.png}
     \caption{N2 Chart Example}
@@
 
+\section{Future Work and Observations}
+Implementation of the overall mission architecture has been successful for the original mission profile.
+Future work includes adapting the mission architecture to the new mission profile from the launch delay.
+For example, it has spawned a tradestudy for rechargable batteries and solar panals.
+However, the original mission architecture does not require extensive rework since many attributes are similar.
+The mission architecture requires only a few sessions between team members to make adaptations.
+All documentation would be automatically updated to reflect these changes per the docs-as-code approach which will eliminate additional work in that category.
+
+Extensions to the DOF data model are also under development for enabling additional use cases, such as the N2 chart, for cubesat systems engineering \cite{sealion_dof}.
+This extended data model would serve as a self-describing specification that new cubesat projects could adopt for their own cubesat missions, whereby the SeaLion mission would serve as the first reference implementation.
+Additionally, training material will be developed around this new data model in efforts to help guide incoming CubeSat developers.
+Multiple team members of the SeaLion mission have been able to quickly learn the methodology of using the docs-as-code approach within a short training session with an experienced member.
+However, a fully realized tutorial would be beneficial to allow for self-learning.
+Current guides are lists of definitions and format guides rather than a step by step tutorial on using the approach which has caused confusion amongst members that attempted to self-learn.
+
+Additionally, observations from the implmentation of the docs-as-code approach noted that an effective communication plan between team members is key to the overall effectiveness of the mission architecture.
+Team members focused on specific parts of the CubeSat's development (e.g., structure, payload, etc.) are required to add all necessary content to the architecture.
+If team members are unavailable due to other more important obligations (e.g., universtiy courses), it can cause considerable delays in the architecture's completion.
+The SeaLion mission architecture team necessitated frequent meetings with individual team members to gather the necessary content for the architecture to capture all legacy work.
+Legacy work being design decisions made prior to the architecture model's introduction.
+In an ideal case, a mission architecture would be formatted prior to any major design decision so that all team members can work directly to the architecture model rather than adapting legacy work to the model.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
-The SeaLion mission architecture team used MBSE with docs-as-code approach to the SeaLion project.
-This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for the CubeSat developers.
-This is particularly important when CubeSat projects are growing more numerous and with many of their respective team members being new to space systems development.
-It has accomplished the ability to create individual elements of the architecture in an easily human readable code that is also easy to make revisions to.
-Even for those who are unfamiliar with coding software or methods.
+The SeaLion mission architecture team used MBSE with a docs-as-code approach to the SeaLion project.
+This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for CubeSat developers.
+This is particularly important when CubeSat projects are growing more numerous with many of their respective team members being new to space systems development.
+The methodology presented herein has accomplished the ability to create individual elements of the architecture in an human readable code that is also easy to make revisions to and persists on a local file system.
+Even for those who are unfamiliar with coding software or methodology.
 Thus, minimal training is required for usage.
-It can also generate documents for easy presentation as well.
-Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.
+The mission architecture presented captures the necessary information required of its original mission profile while also generating documents for easy presentation as well.
+Further work is required to create tutorials to train new users in a self-learning environment.
+Other future work includes the components implementation to faciliate interfaces and junctions for proper component relationships and planning, DOF data model extensions, and adaption to the new mission profile.
+Additionally, new users to this methodology should establish an effective team communication plan at the beginning of a project in order to prevent delays or rework in the creation of a mission architecture.
 
@@
 VLEO &	Very Low Earth Orbit\\
-WFF &	Wallops Flight Facility 
+WFF &	Wallops Flight Facility\\
+XMI & XML Metadata Interchange
 \end{tabular}
